### 2019-11-19 scripts/manuscript.Rmd
Added folders and manuscript

---
title             : "Personality and political beliefs across the lifespan"
shorttitle        : "PERSONALITY AND POLITICAL BELIEFS"
author: 
  - name          : "Sarah Dimakis"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "University of Oregon, Eugene, OR"
    email         : "sdimakis@uoregon.edu"
  - name          : "Meghan Siritzky"
    affiliation   : "1"
  - name          : "Jamie Yellowtail"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "University of Oregon"
authornote: |
  This project was completed as part of the EDLD Introduction to Data Science class at the University of Oregon.
abstract: |
  Someone should write an abstract

keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(papaja)
library(rio)
library(here)
library(tidyverse)

data <- import(here("data", "EPB.csv"), setclass = "tbl_df")
```

```{r analysis-preferences}
knitr::opts_chunk$set(echo = FALSE)

```

```{r cleaning}

```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2019-11-19 scripts/manuscript.tex
Added folders and manuscript

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Personality and political beliefs across the lifespan},
            pdfauthor={Sarah Dimakis, Meghan Siritzky, \& Jamie Yellowtail},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Personality and political beliefs across the lifespan}
    \author{Sarah Dimakis\textsuperscript{1}, Meghan Siritzky\textsuperscript{1}, \&
Jamie Yellowtail\textsuperscript{1}}
    \date{}

\shorttitle{PERSONALITY AND POLITICAL BELIEFS}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Oregon}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers

\authornote{This project was completed as part of the EDLD
Introduction to Data Science class at the University of Oregon.

Correspondence concerning this article should be addressed to Sarah
Dimakis, University of Oregon, Eugene, OR. E-mail:
\href{mailto:sdimakis@uoregon.edu}{\nolinkurl{sdimakis@uoregon.edu}}}

\abstract{
Someone should write an abstract

}

\begin{document}
\maketitle

\section{Methods}\label{methods}

We report how we determined our sample size, all data exclusions (if
any), all manipulations, and all measures in the study.

\subsection{Participants}\label{participants}

\subsection{Material}\label{material}

\subsection{Procedure}\label{procedure}

\subsection{Data analysis}\label{data-analysis}

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
\emph{here} (Version 0.1; Müller, 2017), \emph{papaja} (Version
0.1.0.9842; Aust \& Barth, 2018), and \emph{rio} (Version 0.5.16; C.-h.
Chan, Chan, Leeper, \& Becker, 2018) for all our analyses.

\section{Results}\label{results}

\section{Discussion}\label{discussion}

\newpage

\section{References}\label{references}

\begingroup
\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-R-papaja}{}
Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with
R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\hypertarget{ref-R-rio}{}
Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018).
\emph{Rio: A swiss-army knife for data file i/o}.

\hypertarget{ref-R-here}{}
Müller, K. (2017). \emph{Here: A simpler way to find your files}.
Retrieved from \url{https://CRAN.R-project.org/package=here}

\hypertarget{ref-R-base}{}
R Core Team. (2019). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}

\endgroup

\end{document}

### 2019-11-19 scripts/manuscript.Rmd
filter, mutate, and select

@@
 library(tidyverse)
+library(psych)
 
-data <- import(here("data", "EPB.csv"), setclass = "tbl_df")
+data <- import(here("data", "EPB.sav"), setclass = "tbl_df")
 ```
@@
 
-```{r cleaning}
+```{r filter}
+#Removing particpants from the sample
 
+#filter out preview mode (not real participants) and those who did not complete the survey
+data <- data %>% 
+  filter(DistributionChannel != "preview" & Progress == 100)
+
+#filter out those who did not pass the attention checks
+data <- data %>% 
+  filter(Q6_8 == 6 & Q5_14 == 3)
+
+#filter out those who took the survey too quickly (the time cut offs were predetermined and based on which condition the participant was randomly assigned to)
+data <- data %>% 
+  pivot_longer(cols = Video_DO_V4:Video_DO_V1, 
+               names_to = "Video_DO", 
+               values_to = "Value",
+               names_prefix = "Video_DO_",
+               values_drop_na = TRUE) %>% 
+  filter(Video_DO == 'V1' & Duration__in_seconds_ >316 | 
+           Video_DO == 'V2' & Duration__in_seconds_ > 340 | 
+           Video_DO == 'V3' & Duration__in_seconds_ > 398 |
+           Video_DO == 'V4' & Duration__in_seconds_ > 666 | 
+           Video_DO == 'V5' & Duration__in_seconds_ > 565 | 
+           Video_DO == 'V6' & Duration__in_seconds_ > 538) %>% 
+  filter(Duration__in_seconds_ < 5000) #this person spent too long taking the survey
+```
+
+```{r aggregrateSEC}
+
+#Aggregating the social and economic conservationism scale (SECs)
+items <- c("Q3_1", "Q3_2","Q3_3","Q3_4","Q3_5","Q3_6","Q3_7","Q3_8","Q3_9","Q3_10","Q3_11","Q3_12" )
+
+#econonmic conservatism subscale 
+scaleKey <- c(0, 1, 0, 0, -1, 1, 0, 0, 1, 1, 0, 0)
+economic <- scoreItems(keys = scaleKey, items = data[items], 
+  totals = FALSE, missing = FALSE, min = 0, max = 100)
+data <- data %>% 
+  mutate(SEC_economic_conservatism = economic$scores[,1])
+
+#social conservatism subscale
+scaleKey <- c(-1, 0, 1, 1, 0, 0, 1, 1, 0, 0, 1, 1)
+social <- scoreItems(keys = scaleKey, items = data[items], 
+  totals = FALSE, missing = FALSE, min = 0, max = 100)
+data <- data %>% 
+  mutate(SEC_social_conservatism = social$scores[,1])
+```
+
+```{r aggregateTIPI}
+
+#Aggregating big 5 traits (TIPI)
+items <- c("Q4_1", "Q4_2", "Q4_3", "Q4_4", "Q4_5", "Q4_6", "Q4_7", "Q4_8", "Q4_9", "Q4_10")
+
+#Extraversion
+scaleKey <- c(1, 0, 0, 0, 0, -1, 0, 0, 0, 0)
+extraversion <- scoreItems(keys = scaleKey, items = data[items], 
+  totals = FALSE, missing = FALSE, min = 1, max = 7)
+data <- data %>% 
+  mutate(Extraversion = extraversion$scores[,1])
+
+#Agreeableness
+scaleKey <- c(0, -1, 0, 0, 0, 0, 1, 0, 0, 0)
+agree <- scoreItems(keys = scaleKey, items = data[items], 
+  totals = FALSE, missing = FALSE, min = 1, max = 7)
+data <- data %>% 
+  mutate(Agreeableness = agree$scores[,1])
+
+#Conscientiousness
+scaleKey <- c(0, 0, 1, 0, 0, 0, 0, -1, 0, 0)
+consc <- scoreItems(keys = scaleKey, items = data[items], 
+  totals = FALSE, missing = FALSE, min = 1, max = 7)
+data <- data %>% mutate(Conscientiousness = consc$scores[,1])
+
+#Emotional stability
+scaleKey <- c(0, 0, 0, -1, 0, 0, 0, 0, 1, 0)
+emo <- scoreItems(keys = scaleKey, items = data[items], 
+  totals = FALSE, missing = FALSE, min = 1, max = 7)
+data <- data %>% 
+  mutate(Emotional_stability = emo$scores[,1])
+
+#Openness to experiences
+scaleKey <- c(0, 0, 0, 0, 5, 0, 0, 0, 0, -1)
+open <- scoreItems(keys = scaleKey, items = data[items], 
+  totals = FALSE, missing = FALSE, min = 1, max = 7)
+data <- data %>% 
+  mutate(Openness_to_experiences = open$scores[,1])
+```
+
+```{r select}
+#selecting the variables that we want to use
+data <- data %>% 
+  select(ResponseId, Q7, Q8, Q9, Q10, Q11,
+         SEC_economic_conservatism, SEC_social_conservatism,
+         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
+  rename(Gender = Q7, 
+         Age = Q8, 
+         Ethnicity = Q9, 
+         Political_orientation = Q10,
+         Political_affiliation = Q11,
+         id = ResponseId) %>% 
+  janitor::clean_names() %>% 
+  characterize()
 ```

### 2019-11-19 scripts/manuscript.tex
filter, mutate, and select

@@
 We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
-\emph{here} (Version 0.1; Müller, 2017), \emph{papaja} (Version
-0.1.0.9842; Aust \& Barth, 2018), and \emph{rio} (Version 0.5.16; C.-h.
-Chan, Chan, Leeper, \& Becker, 2018) for all our analyses.
+\emph{dplyr} (Version 0.8.3; Wickham, François, Henry, \& Müller, 2019),
+\emph{forcats} (Version 0.4.0; Wickham, 2019a), \emph{ggplot2} (Version
+3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017),
+\emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{purrr}
+(Version 0.3.3; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1;
+Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; C.-h.
+Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0;
+Wickham, 2019b), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
+\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and
+\emph{tidyverse} (Version 1.2.1; Wickham, 2017) for all our analyses.
 
@@
 
+\hypertarget{ref-R-purrr}{}
+Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
+tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
 \hypertarget{ref-R-here}{}
@@
 Retrieved from \url{https://CRAN.R-project.org/package=here}
+
+\hypertarget{ref-R-tibble}{}
+Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
+Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
@@
 
+\hypertarget{ref-R-ggplot2}{}
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
+Springer-Verlag New York. Retrieved from
+\url{https://ggplot2.tidyverse.org}
+
+\hypertarget{ref-R-tidyverse}{}
+Wickham, H. (2017). \emph{Tidyverse: Easily install and load the
+'tidyverse'}. Retrieved from
+\url{https://CRAN.R-project.org/package=tidyverse}
+
+\hypertarget{ref-R-forcats}{}
+Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical
+variables (factors)}. Retrieved from
+\url{https://CRAN.R-project.org/package=forcats}
+
+\hypertarget{ref-R-stringr}{}
+Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for
+common string operations}. Retrieved from
+\url{https://CRAN.R-project.org/package=stringr}
+
+\hypertarget{ref-R-tidyr}{}
+Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}.
+Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\hypertarget{ref-R-dplyr}{}
+Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr:
+A grammar of data manipulation}. Retrieved from
+\url{https://CRAN.R-project.org/package=dplyr}
+
+\hypertarget{ref-R-readr}{}
+Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read
+rectangular text data}. Retrieved from
+\url{https://CRAN.R-project.org/package=readr}
+
 \endgroup

### 2019-11-19 scripts/manuscript.Rmd
tidying (pivot_longer)

@@
 
-#Aggregating the social and economic conservationism scale (SECs)
+#Aggregating the social and economic conservationism scale (SECs) using scoreItems from the psych package and mutate from dplyr
 items <- c("Q3_1", "Q3_2","Q3_3","Q3_4","Q3_5","Q3_6","Q3_7","Q3_8","Q3_9","Q3_10","Q3_11","Q3_12" )
@@
 
-#Aggregating big 5 traits (TIPI)
+#Aggregating big 5 traits (TIPI) using scoreItems from the psych package and mutate from dplyr
 items <- c("Q4_1", "Q4_2", "Q4_3", "Q4_4", "Q4_5", "Q4_6", "Q4_7", "Q4_8", "Q4_9", "Q4_10")
@@
 ```{r select}
-#selecting the variables that we want to use
+#selecting the variables that we want to use, cleaning, and characterizing dataset
 data <- data %>% 
@@
   characterize()
+```
+
+```{r tidying}
+#last step is to tidy our data
+tidy <- data %>% 
+  pivot_longer(cols = c(sec_economic_conservatism, sec_social_conservatism),
+               names_to = "conservatism_type",
+               names_prefix = "sec_",
+               values_to = "conservatism_score") %>% 
+  pivot_longer(cols = agreeableness:emotional_stability,
+               names_to = "personality_trait",
+               values_to = "personality_score")
 ```

### 2019-11-19 scripts/manuscript.Rmd
figure1 personality traits across the lifespan)

@@
   janitor::clean_names() %>% 
-  characterize()
+  characterize() %>% 
+  mutate(age = as.numeric(age))
 ```
@@
 
+```{r figure1}
+ggplot(tidy, aes(x = age, y = personality_score, color = personality_trait)) +
+  geom_smooth(se=FALSE, method = "lm")+
+  labs(title = "Personality traits across the lifespan", subtitle = "Big 5 traits self-reported by adults aged 20-68",
+       x= "Age", y = "How strongly participants identify with the personality trait", 
+       color = "Personality Trait")+
+  theme_classic()+
+  scale_color_manual(values = c("red", "orange", "yellow","green", "blue"),
+                     labels=c("Agreeableness", "Conscientiousness", 
+                              "Emotional Stability", "Extraversion",
+                             "Openness to experiences"))
+
+```
 # Methods

### 2019-11-19 scripts/manuscript.tex
figure1 personality traits across the lifespan)

@@
 
-\section{Methods}\label{methods}
-
+\includegraphics{manuscript_files/figure-latex/figure1-1.pdf} \# Methods
 We report how we determined our sample size, all data exclusions (if
@@
 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017),
-\emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{purrr}
-(Version 0.3.3; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1;
-Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; C.-h.
-Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0;
-Wickham, 2019b), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
-\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and
-\emph{tidyverse} (Version 1.2.1; Wickham, 2017) for all our analyses.
+\emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych}
+(Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.3; Henry \&
+Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \&
+Francois, 2018), \emph{rio} (Version 0.5.16; C.-h. Chan, Chan, Leeper,
+\& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019b),
+\emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr}
+(Version 1.0.0; Wickham \& Henry, 2019), and \emph{tidyverse} (Version
+1.2.1; Wickham, 2017) for all our analyses.
 
@@
 
+\hypertarget{ref-R-psych}{}
+Revelle, W. (2018). \emph{Psych: Procedures for psychological,
+psychometric, and personality research}. Evanston, Illinois:
+Northwestern University. Retrieved from
+\url{https://CRAN.R-project.org/package=psych}
+
 \hypertarget{ref-R-ggplot2}{}

### 2019-11-20 scripts/manuscript.Rmd
added table 1 of personality traits across age groups

@@
 ```
+
+```{r table1, echo = FALSE, results = "asis"}
+tidy_table <- tidy %>% 
+  mutate(age = case_when(       
+      age <= 30 & age >= 20 ~ "[20-30]",
+      age <= 40 & age >= 31 ~ "[31-40]",
+      age <= 50 & age >= 41 ~ "[41-50]",
+      age <= 60 & age >= 51 ~ "[51-60]",
+      TRUE ~ "[61-68]"))
+tidy_table <- tidy_table %>% 
+  group_by(personality_trait, age) %>% 
+  summarize(mean_personality_score = mean(personality_score)) %>% 
+  pivot_wider(names_from = age, values_from = mean_personality_score) %>% 
+  rename("Personality Trait" = personality_trait)
+
+apa_table(tidy_table, 
+            caption = "Mean Personality Trait Scores Across the Lifespan",
+          col_spanners = list(`Age Group` = c(2, 6)),
+          note = "Personality trait scores reported on a 1-7 scale."
+)
+```
+
 # Methods

### 2019-11-20 scripts/manuscript.Rmd
table 1 changed age groups

--- 2019-11-19 scripts/manuscript.Rmd
@@
 ```
+
+```{r table1, echo = FALSE, results = "asis"}
+tidy_table <- tidy %>% 
+  mutate(age = case_when(       
+      age <= 29 & age >= 20 ~ "[20-29]",
+      age <= 39 & age >= 30 ~ "[30-39]",
+      age <= 49 & age >= 40 ~ "[40-49]",
+      age <= 59 & age >= 50 ~ "[50-59]",
+      TRUE ~ "[60-68]"))
+tidy_table <- tidy_table %>% 
+  group_by(personality_trait, age) %>% 
+  summarize(mean_personality_score = mean(personality_score)) %>% 
+  pivot_wider(names_from = age, values_from = mean_personality_score) %>% 
+  rename("Personality Trait" = personality_trait)
+
+apa_table(tidy_table, 
+            caption = "Mean Personality Trait Scores Across the Lifespan",
+          col_spanners = list(`Age Group` = c(2, 6)),
+          note = "Personality trait scores reported on a 1-7 scale."
+)
+```
+
 # Methods

### 2019-11-20 scripts/manuscript.Rmd
figure 2
Created figure 2 to display conservatism over time by gender. Also mutated 'conservatism type' variable to factor.

@@
                values_to = "conservatism_score") %>% 
+  mutate(conservatism_type = factor(conservatism_type, 
+                          labels = c("Economic",
+                                     "Social"))) %>%
   pivot_longer(cols = agreeableness:emotional_stability,
@@
 
+```{r figure2}
+ggplot(tidy, aes(x = age, y = conservatism_score, color = conservatism_type)) +
+  geom_smooth(se=FALSE, method = "lm")+
+  labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
+       x= "Age", y = "Conservatism Score (higher = more conservative)",
+       color = "Conservatism Type")+
+  theme_minimal()+
+  facet_wrap(~gender)
+
+```
+
+```{r}
+
+```
+
 # Methods

### 2019-11-20 scripts/manuscript.Rmd
messy data (pivot_wider)
Utilized pivot_wider() to expand types of conservatism and personality traits across columns

@@
   geom_smooth(se=FALSE, method = "lm")+
+  scale_color_viridis_d() +
   labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
@@
 
-```{r}
+```{r messy_data}
+messy <- tidy %>% 
+  pivot_wider(
+    names_from = conservatism_type, 
+    values_from = conservatism_score) %>%
+   pivot_wider(
+     names_from = personality_trait,
+     values_from = personality_score)
 

### 2019-11-20 scripts/manuscript.Rmd
figure captions, recoding variables

--- 2019-11-20 scripts/manuscript.Rmd
@@
 abstract: |
-  Someone should write an abstract
+  Here is where we will write our abstract.
 
@@
                values_to = "conservatism_score") %>% 
+  mutate(conservatism_type = recode(conservatism_type, `economic_conservatism` = "Economic conservatism",
+                                    `social_conservatism` = "Social conservatism")) %>%
   pivot_longer(cols = agreeableness:emotional_stability,
                names_to = "personality_trait",
-               values_to = "personality_score")
-```
-
-```{r figure1}
-ggplot(tidy, aes(x = age, y = personality_score, color = personality_trait)) +
-  geom_smooth(se=FALSE, method = "lm")+
-  labs(title = "Personality traits across the lifespan", subtitle = "Big 5 traits self-reported by adults aged 20-68",
-       x= "Age", y = "How strongly participants identify with the personality trait", 
-       color = "Personality Trait")+
-  theme_classic()+
-  scale_color_manual(values = c("red", "orange", "yellow","green", "blue"),
-                     labels=c("Agreeableness", "Conscientiousness", 
-                              "Emotional Stability", "Extraversion",
-                             "Openness to experiences"))
-
+               values_to = "personality_score") %>% 
+  mutate(personality_trait = recode(personality_trait, `agreeableness` = "Agreeableness",
+                                    `conscientiousness` = "Conscientiousness",
+                                    `openness_to_experiences` = "Openness to experiences",
+                                    `extraversion` = "Extraversion",
+                                    `emotional_stability` = "Emotional stability"))
 ```
@@
 
+```{r figure1, fig.cap= "Generally, older adults rated themselves higher on each of the big five personality traits than young adults. This sample was unexpectedly introverted."}
+
+ggplot(tidy, aes(x = age, y = personality_score, color = personality_trait)) +
+  geom_smooth(se=FALSE, method = "lm")+
+  labs(title = "Personality traits across the lifespan", subtitle = "Big 5 traits self-reported by adults aged 20-68",
+       x= "Age", y = "How strongly participants identify with the personality trait", 
+       color = "Personality Trait")+
+  theme_minimal()+
+  scale_color_viridis_d()
+
+```
+
+```{r figure2, fig.cap= "Generally, older adults reported stronger socially and fiscally conservative beliefs compared to young adults.
+This increase in conservative beliefs as we age may be more extreme for socially conservative beliefs than for fiscally conservate beliefs."}
+
+ggplot(tidy, aes(x = age, y = conservatism_score, color = conservatism_type)) +
+  geom_smooth(se=FALSE, method = "lm")+
+  scale_color_viridis_d() +
+  labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
+       x= "Age", y = "Conservatism Score (higher = more conservative)",
+       color = "Conservatism Type")+
+  theme_minimal()+
+  facet_wrap(~gender)
+```
+
+```{r messy_data}
+messy <- tidy %>% 
+  pivot_wider(
+    names_from = conservatism_type, 
+    values_from = conservatism_score) %>%
+   pivot_wider(
+     names_from = personality_trait,
+     values_from = personality_score)
+
+#we can use this messy data to run lm models
+```
+
 # Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
 

### 2019-11-20 scripts/manuscript.tex
figure captions, recoding variables

@@
 \abstract{
-Someone should write an abstract
+Here is where we will write our abstract.
 
@@
 
-\includegraphics{manuscript_files/figure-latex/figure1-1.pdf} \# Methods
-We report how we determined our sample size, all data exclusions (if
-any), all manipulations, and all measures in the study.
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:table1}Mean Personality Trait Scores Across the Lifespan}
+\begin{tabular}{llllll}
+\toprule
+ & \multicolumn{5}{c}{Age Group} \\
+\cmidrule(r){2-6}
+Personality Trait & \multicolumn{1}{c}{[20-29]} & \multicolumn{1}{c}{[30-39]} & \multicolumn{1}{c}{[40-49]} & \multicolumn{1}{c}{[50-59]} & \multicolumn{1}{c}{[60-68]}\\
+\midrule
+Agreeableness & 4.70 & 5.11 & 5.58 & 6.05 & 6.08\\
+Conscientiousness & 5.24 & 5.60 & 5.89 & 5.71 & 5.88\\
+Emotional stability & 4.22 & 4.91 & 4.97 & 5.79 & 5.71\\
+Extraversion & 3.14 & 3.42 & 3.37 & 4.18 & 3.96\\
+Openness to experiences & 5.10 & 5.22 & 4.97 & 5.50 & 6.04\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Personality trait scores reported on a 1-7 scale.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/figure1-1.pdf}
+\caption{\label{fig:figure1}Generally, older adults rated themselves higher
+on each of the big five personality traits than young adults. This
+sample was unexpectedly introverted.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
+\caption{\label{fig:figure2}Generally, older adults reported stronger
+socially and fiscally conservative beliefs compared to young adults.
+This increase in conservative beliefs as we age may be more extreme for
+socially conservative beliefs than for fiscally conservate beliefs.}
+\end{figure}
+
+\section{Methods}\label{methods}
 

### 2019-11-23 scripts/manuscript.Rmd
one comment for improving efficiency (slightly)
library(grid) to provide space between facet_wrap, spacing the x-axis

@@
 library(psych)
+#install.packages("ggsave")
+library(grid)
 
@@
                values_drop_na = TRUE) %>%
-  filter(Video_DO == 'V1' & Duration__in_seconds_ >316 | 
+  filter(Video_DO == 'V1' & Duration__in_seconds_ > 316 |
            Video_DO == 'V2' & Duration__in_seconds_ > 340 |
@@
 scaleKey <- c(0, 1, 0, 0, -1, 1, 0, 0, 1, 1, 0, 0)
-economic <- scoreItems(keys = scaleKey, items = data[items], 
-  totals = FALSE, missing = FALSE, min = 0, max = 100)
+economic <- scoreItems(
+  keys = scaleKey,
+  items = data[items],
+  totals = FALSE,
+  missing = FALSE,
+  min = 0, max = 100)
 data <- data %>% 
@@
 scaleKey <- c(-1, 0, 1, 1, 0, 0, 1, 1, 0, 0, 1, 1)
-social <- scoreItems(keys = scaleKey, items = data[items], 
-  totals = FALSE, missing = FALSE, min = 0, max = 100)
+social <- scoreItems(
+  keys = scaleKey,
+  items = data[items],
+  totals = FALSE,
+  missing = FALSE,
+  min = 0, 
+  max = 100)
 data <- data %>% 
@@
 scaleKey <- c(1, 0, 0, 0, 0, -1, 0, 0, 0, 0)
-extraversion <- scoreItems(keys = scaleKey, items = data[items], 
-  totals = FALSE, missing = FALSE, min = 1, max = 7)
+extraversion <- scoreItems(
+  keys = scaleKey,
+  items = data[items],
+  totals = FALSE,
+  missing = FALSE,
+  min = 1, max = 7)
 data <- data %>% 
@@
 scaleKey <- c(0, -1, 0, 0, 0, 0, 1, 0, 0, 0)
-agree <- scoreItems(keys = scaleKey, items = data[items], 
-  totals = FALSE, missing = FALSE, min = 1, max = 7)
+agree <- scoreItems(
+  keys = scaleKey,
+  items = data[items],
+  totals = FALSE,
+  missing = FALSE,
+  min = 1,
+  max = 7)
 data <- data %>%
@@
 scaleKey <- c(0, 0, 1, 0, 0, 0, 0, -1, 0, 0)
-consc <- scoreItems(keys = scaleKey, items = data[items], 
-  totals = FALSE, missing = FALSE, min = 1, max = 7)
-data <- data %>% mutate(Conscientiousness = consc$scores[,1])
+consc <- scoreItems(
+  keys = scaleKey,
+  items = data[items],
+  totals = FALSE,
+  missing = FALSE,
+  min = 1,
+  max = 7)
+data <- data %>%
+  mutate(Conscientiousness = consc$scores[,1])
 
@@
 scaleKey <- c(0, 0, 0, -1, 0, 0, 0, 0, 1, 0)
-emo <- scoreItems(keys = scaleKey, items = data[items], 
-  totals = FALSE, missing = FALSE, min = 1, max = 7)
+emo <- scoreItems(
+  keys = scaleKey,
+  items = data[items],
+  totals = FALSE,
+  missing = FALSE,
+  min = 1,
+  max = 7)
 data <- data %>%
@@
 scaleKey <- c(0, 0, 0, 0, 5, 0, 0, 0, 0, -1)
-open <- scoreItems(keys = scaleKey, items = data[items], 
-  totals = FALSE, missing = FALSE, min = 1, max = 7)
+open <- scoreItems(
+  keys = scaleKey,
+  items = data[items],
+  totals = FALSE,
+  missing = FALSE,
+  min = 1, max = 7)
 data <- data %>%
@@
   select(ResponseId, Q7, Q8, Q9, Q10, Q11,
-         SEC_economic_conservatism, SEC_social_conservatism,
-         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
+         SEC_economic_conservatism,
+         SEC_social_conservatism,
+         Agreeableness,
+         Conscientiousness,
+         Openness_to_experiences,
+         Extraversion,
+         Emotional_stability) %>%
   rename(Gender = Q7,
@@
 tidy <- data %>%
-  pivot_longer(cols = c(sec_economic_conservatism, sec_social_conservatism),
+  pivot_longer(cols = c(
+    sec_economic_conservatism,
+    sec_social_conservatism),
     names_to = "conservatism_type",
@@
     values_to = "conservatism_score") %>% 
-  mutate(conservatism_type = recode(conservatism_type, `economic_conservatism` = "Economic conservatism",
+  mutate(conservatism_type = recode(
+    conservatism_type, 
+    `economic_conservatism` = "Economic conservatism",
     `social_conservatism` = "Social conservatism")) %>%
@@
                values_to = "personality_score") %>%
-  mutate(personality_trait = recode(personality_trait, `agreeableness` = "Agreeableness",
+  mutate(personality_trait =
+           recode(personality_trait,
+                  `agreeableness` = "Agreeableness",
                   `conscientiousness` = "Conscientiousness",
@@
           col_spanners = list(`Age Group` = c(2, 6)),
-          note = "Personality trait scores reported on a 1-7 scale."
-)
+          note = "Personality trait scores reported on a 1-7 scale.")
 ```
@@
 ggplot(tidy, aes(x = age, y = personality_score, color = personality_trait)) +
-  geom_smooth(se=FALSE, method = "lm")+
-  labs(title = "Personality traits across the lifespan", subtitle = "Big 5 traits self-reported by adults aged 20-68",
-       x= "Age", y = "How strongly participants identify with the personality trait", 
-       color = "Personality Trait")+
-  theme_minimal()+
+  geom_smooth(se = FALSE, method = "lm") +
+  labs(
+    title = "Personality traits across the lifespan",
+    subtitle = "Big 5 traits self-reported by adults aged 20-68",
+    x = "Age", y = "How strongly participants identify with the personality trait",
+    color = "Personality Trait") +
+  theme_minimal() +
   scale_color_viridis_d()
@@
 ggplot(tidy, aes(x = age, y = conservatism_score, color = conservatism_type)) +
-  geom_smooth(se=FALSE, method = "lm")+
+  geom_smooth(se=FALSE, method = "lm") +
   scale_color_viridis_d() +
-  labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
-       x= "Age", y = "Conservatism Score (higher = more conservative)",
-       color = "Conservatism Type")+
-  theme_minimal()+
+  labs(
+    title = "Conservatism across the lifespan (adults aged 20-68)",
+    subtitle = "Difference in Economic and Social Conservatism by Gender",
+    x = "Age", y = "Conservatism Score (higher = more conservative)",
+    color = "Conservatism Type") +
+  theme_minimal() +
+  theme(panel.spacing = unit(2, "lines")) +
   facet_wrap(~gender)
@@
     values_from = personality_score)
-
 #we can use this messy data to run lm models

### 2019-11-27 scripts/manuscript.Rmd
script feedback

--- 2019-11-20 scripts/manuscript.Rmd
@@
   mutate(Openness_to_experiences = open$scores[,1])
+
 ```
@@
   mutate(age = as.numeric(age))
+
+#Are you going to include the ethnicity data in later plots? If not, you could just select the other columns. 
 ```

### 2019-11-27 scripts/manuscript.Rmd

@@
 )
+
+#This table is helpful and conveys a lot of information in a very clear format. 
 ```
@@
   facet_wrap(~gender)
+
+#You could use this same plot and facet wrap by ethnicity instead of gender. 
 ```

### 2019-12-01 scripts/manuscript.Rmd
changed figures & added tables & ran multiple regressions

--- 2019-11-27 scripts/manuscript.Rmd
@@
 library(psych)
+library(knitr)
+library(MBESS)
 
@@
   mutate(Openness_to_experiences = open$scores[,1])
-
 ```
@@
   mutate(age = as.numeric(age))
-
-#Are you going to include the ethnicity data in later plots? If not, you could just select the other columns. 
 ```
@@
 ```{r table1, echo = FALSE, results = "asis"}
-tidy_table <- tidy %>% 
-  mutate(age = case_when(       
-      age <= 29 & age >= 20 ~ "[20-29]",
-      age <= 39 & age >= 30 ~ "[30-39]",
-      age <= 49 & age >= 40 ~ "[40-49]",
-      age <= 59 & age >= 50 ~ "[50-59]",
-      TRUE ~ "[60-68]"))
-tidy_table <- tidy_table %>% 
-  group_by(personality_trait, age) %>% 
+tidy_table_sc <- tidy %>% 
+  filter(conservatism_type == 'Social conservatism') %>% 
+  mutate(conservatism_score = case_when(       
+      conservatism_score <= 19 & conservatism_score >= 0 ~ "[0-19]",
+      conservatism_score <= 39 & conservatism_score >= 20 ~ "[20-39]",
+      conservatism_score <= 59 & conservatism_score >= 40 ~ "[40-59]",
+      conservatism_score <= 79 & conservatism_score >= 60 ~ "[60-79]",
+      TRUE ~ "[80-100]"))
+tidy_table_sc <- tidy_table_sc %>% 
+  group_by(personality_trait, conservatism_score) %>% 
   summarize(mean_personality_score = mean(personality_score)) %>% 
-  pivot_wider(names_from = age, values_from = mean_personality_score) %>% 
-  rename("Personality Trait" = personality_trait)
+  pivot_wider(names_from = conservatism_score, values_from = mean_personality_score)
 
-apa_table(tidy_table, 
-            caption = "Mean Personality Trait Scores Across the Lifespan",
-          col_spanners = list(`Age Group` = c(2, 6)),
-          note = "Personality trait scores reported on a 1-7 scale."
-)
+apa_table(tidy_table_sc, 
+            caption = "Mean Personality Trait Scores by Social Conservatism Score",
+          col_spanners = list(`Social Conservatism Score` = c(2, 6)),
+          note = "Personality trait scores reported on a 1-7 scale.")
+```
+
+```{r table2, echo = FALSE, results = "asis"}
+tidy_table_ec <- tidy %>% 
+  filter(conservatism_type == 'Economic conservatism') %>% 
+  mutate(conservatism_score = case_when(       
+      conservatism_score <= 19 & conservatism_score >= 0 ~ "[0-19]",
+      conservatism_score <= 39 & conservatism_score >= 20 ~ "[20-39]",
+      conservatism_score <= 59 & conservatism_score >= 40 ~ "[40-59]",
+      conservatism_score <= 79 & conservatism_score >= 60 ~ "[60-79]",
+      TRUE ~ "[80-100]"))
+tidy_table_ec <- tidy_table_ec %>% 
+  group_by(personality_trait, conservatism_score) %>% 
+  summarize(mean_personality_score = mean(personality_score)) %>% 
+  pivot_wider(names_from = conservatism_score, values_from = mean_personality_score)
+
+apa_table(tidy_table_ec, 
+            caption = "Mean Personality Trait Scores by Economic Conservatism Score",
+          col_spanners = list(`Economic Conservatism Score` = c(2, 6)),
+          note = "Personality trait scores reported on a 1-7 scale.")
+```
+
+```{r linearmodels_conservatism_ocean, include = FALSE}
+untidy <- tidy %>% 
+  pivot_wider(names_from = conservatism_type, values_from = conservatism_score) %>% 
+  pivot_wider(names_from = personality_trait, values_from = personality_score) %>% 
+  rename(social_conservatism = 'Social conservatism',
+         economic_conservatism = 'Economic conservatism',
+         openness_to_experiences = 'Openness to experiences',
+         emotional_stability = 'Emotional stability')
+
+sc_ocean <- lm(social_conservatism ~ openness_to_experiences + Conscientiousness + Extraversion + Agreeableness + emotional_stability,
+              data = untidy)
+summary(sc_ocean)
+plot(scale(residuals(sc_ocean)) ~ scale(fitted(sc_ocean)), xlab="Social Conservatism Scores", ylab = "Scaled Residuals")
+
+ec_ocean <- lm(economic_conservatism ~ openness_to_experiences + Conscientiousness + Extraversion + Agreeableness + emotional_stability,
+              data = untidy)
+summary(ec_ocean)
+plot(scale(residuals(ec_ocean)) ~ scale(fitted(ec_ocean)), xlab="Economic Conservatism Scores", ylab = "Scaled Residuals")
+```
+
+```{r linearmodels_conservatism_ocean_tables, echo = FALSE, results = "asis"}
+apa_sc_ocean <- apa_print(sc_ocean)
+apa_sc_ocean$table %>% 
+  apa_table(caption = "Regression Table Predicting Social Conservatism From Big-Five Personality Traits.", note = "Residual standard error: 25.13 on 125 degrees of freedom.
+Multiple R-squared: 0.168, Adjusted R-squared: 0.135. F(5, 125): 5.051, p-value: 0.0003.", escape = FALSE)
+
+apa_ec_ocean <- apa_print(ec_ocean)
+apa_ec_ocean$table %>% 
+  apa_table(caption = "Regression Table Predicting Economic Conservatism From Big-Five Personality Traits.", note = "Residual standard error: 21.3 on 125 degrees of freedom.
+Multiple R-squared: 0.081, Adjusted R-squared: 0.044.
+F(5, 125): 2.207, p-value: 0.058.", escape = FALSE)
+```
+
+```{r correlations, include = FALSE}
+set.seed=180
+cor_conservatism <- corr.test(untidy$economic_conservatism, untidy$social_conservatism)
+cor_conservatism
+
+untidy_cor <- untidy %>% 
+  select(-c(1:6))
+cor_conservatism_ocean <- corr.test(untidy_cor)
+cor_conservatism_ocean
+```
+
+```{r correlations heatmap, include = FALSE}
+
 ```
@@
 ```{r figure1, fig.cap= "Generally, older adults rated themselves higher on each of the big five personality traits than young adults. This sample was unexpectedly introverted."}
-
-ggplot(tidy, aes(x = age, y = personality_score, color = personality_trait)) +
+ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +
   geom_smooth(se=FALSE, method = "lm")+
-  labs(title = "Personality traits across the lifespan", subtitle = "Big 5 traits self-reported by adults aged 20-68",
-       x= "Age", y = "How strongly participants identify with the personality trait", 
+  labs(title = "Social Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
+       x= "How strongly participants identify with the personality trait", y = "Social Conservatism", 
        color = "Personality Trait")+
   theme_minimal()+
-  scale_color_viridis_d()
-
+  scale_color_viridis_d() +
+  facet_wrap(~conservatism_type)
 ```
@@
 
-```{r messy_data}
-messy <- tidy %>% 
-  pivot_wider(
-    names_from = conservatism_type, 
-    values_from = conservatism_score) %>%
-   pivot_wider(
-     names_from = personality_trait,
-     values_from = personality_score)
-
-#we can use this messy data to run lm models
-```
-
 # Methods
@@
 # Results
+
+In order to understand the relation between conservatism and personality, we first looked at Big Five personality trait (Openness to Experience, Conscientiousness, Extraversion, Agreeableness, and Emotional Stability) scores across the spectrum of Social Conservatism (Table 1) and Economic Conservatism (Table 2) scores.
+
+To see whether there were significant relations between Social Conservatism and the Big Five, we then ran a multiple regression predicting Social Conservatism from the Big Five personality traits.
+A significant regression equation was found (*F*(5, 125) = 5.051, *p* < .001), with an adjusted $R^2$ of 0.135 (Table 2).
+Thus, personality traits taken together explained 13.48% of variance in Social Conservatism scores.
+Participants' predicted Social Conservatism scores were equal to 25.82 - 3.73(Openness to Experience) + 0.07(Conscientiousness) + 1.56(Extraversion) + 3.93(Agreeableness) + 4.30(Emotional Stability).
+Agreeableness and Emotional Stability were significant predictors of Social Conservatism.
+
+To see whether there were significant relations between Economic Conservatism and the Big Five, we then ran a multiple regression predicting Economic Conservatism from the Big Five personality traits.
+No significant regression equation was found (*F*(5, 125) = 2.207, *p* = .058) (Table 3).
+Thus, personality traits taken together did not significantly explain variance in Economic Conservatism scores.
+However, Openness to Experience was a significant predictor of Economic Conservatism.
+
+To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be r = 0.65.
 

### 2019-12-01 scripts/manuscript.Rmd
updates on results section

@@
 
-```{r correlations, include = FALSE}
+```{r correlations, echo = FALSE, results = "asis"}
 set.seed=180
@@
 untidy_cor <- untidy %>% 
-  select(-c(1:6))
-cor_conservatism_ocean <- corr.test(untidy_cor)
-cor_conservatism_ocean
+  select(-c(1:6)) %>% 
+  rename('Social conservatism' = 'social_conservatism',
+         'Economic conservatism' = 'economic_conservatism',
+         'Openness to experiences' = 'openness_to_experiences',
+         'Emotional stability' = 'emotional_stability')
+cor_conservatism_ocean <- round(cor(untidy_cor),2)
+upper_s<-cor_conservatism_ocean
+upper_s[upper.tri(cor_conservatism_ocean)]<-""
+upper_s<-as.data.frame(upper_s) %>%
+  apa_table(
+    caption = "Correlation Matrix for Conservatism and Big Five Personality Traits",
+  landscape = TRUE,
+  font_size = "tiny")
 ```
@@
 
-```{r figure1, fig.cap= "Generally, older adults rated themselves higher on each of the big five personality traits than young adults. This sample was unexpectedly introverted."}
+```{r figure1}
 ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +
   geom_smooth(se=FALSE, method = "lm")+
-  labs(title = "Social Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
-       x= "How strongly participants identify with the personality trait", y = "Social Conservatism", 
+  labs(title = "Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
+       x= "How strongly participants identify with the personality trait", y = "Conservatism", 
        color = "Personality Trait")+
@@
 To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be r = 0.65.
+Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits.
 

### 2019-12-01 scripts/manuscript.Rmd
added heatmap

@@
 library(MBESS)
+library(viridis)
 
@@
 
-```{r correlations, echo = FALSE, results = "asis"}
-set.seed=180
-cor_conservatism <- corr.test(untidy$economic_conservatism, untidy$social_conservatism)
-cor_conservatism
-
-untidy_cor <- untidy %>% 
-  select(-c(1:6)) %>% 
-  rename('Social conservatism' = 'social_conservatism',
-         'Economic conservatism' = 'economic_conservatism',
-         'Openness to experiences' = 'openness_to_experiences',
-         'Emotional stability' = 'emotional_stability')
-cor_conservatism_ocean <- round(cor(untidy_cor),2)
-upper_s<-cor_conservatism_ocean
-upper_s[upper.tri(cor_conservatism_ocean)]<-""
-upper_s<-as.data.frame(upper_s) %>%
-  apa_table(
-    caption = "Correlation Matrix for Conservatism and Big Five Personality Traits",
-  landscape = TRUE,
-  font_size = "tiny")
-```
-
-```{r correlations heatmap, include = FALSE}
-
-```
-
-```{r figure1}
-ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +
-  geom_smooth(se=FALSE, method = "lm")+
-  labs(title = "Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
-       x= "How strongly participants identify with the personality trait", y = "Conservatism", 
-       color = "Personality Trait")+
-  theme_minimal()+
-  scale_color_viridis_d() +
-  facet_wrap(~conservatism_type)
-```
-
-```{r figure2, fig.cap= "Generally, older adults reported stronger socially and fiscally conservative beliefs compared to young adults.
-This increase in conservative beliefs as we age may be more extreme for socially conservative beliefs than for fiscally conservate beliefs."}
-
-ggplot(tidy, aes(x = age, y = conservatism_score, color = conservatism_type)) +
-  geom_smooth(se=FALSE, method = "lm")+
-  scale_color_viridis_d() +
-  labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
-       x= "Age", y = "Conservatism Score (higher = more conservative)",
-       color = "Conservatism Type")+
-  theme_minimal()+
-  facet_wrap(~gender)
-```
-
 # Methods
@@
 <div id = "refs"></div>
+
+```{r correlations, echo = FALSE, results = "asis"}
+set.seed=180
+cor_conservatism <- corr.test(untidy$economic_conservatism, untidy$social_conservatism)
+cor_conservatism
+
+untidy_cor <- untidy %>% 
+  select(-c(1:6)) %>% 
+  rename('Social conservatism' = 'social_conservatism',
+         'Economic conservatism' = 'economic_conservatism',
+         'Openness to experiences' = 'openness_to_experiences',
+         'Emotional stability' = 'emotional_stability')
+cor_conservatism_ocean <- round(cor(untidy_cor),2)
+upper_s<-cor_conservatism_ocean
+upper_s[upper.tri(cor_conservatism_ocean)]<-""
+upper_s<-as.data.frame(upper_s) %>%
+  apa_table(
+    caption = "Correlation Matrix for Conservatism and Big Five Personality Traits",
+  landscape = TRUE,
+  font_size = "tiny")
+
+heatmap(cor_conservatism_ocean,
+        Rowv = NA,
+        Colv = NA,
+        main = "Correlation Heatmap",
+        margins = c(15,15),
+        col = viridis(100, direction = -1))
+```
+
+```{r figure1, fig.cap= ""}
+ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +
+  geom_smooth(se=FALSE, method = "lm")+
+  labs(title = "Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
+       x= "How strongly participants identify with the personality trait", y = "Conservatism", 
+       color = "Personality Trait")+
+  theme_minimal()+
+  scale_color_viridis_d() +
+  facet_wrap(~conservatism_type)
+```
+
+```{r figure2, fig.cap= "Generally, older adults reported stronger socially and fiscally conservative beliefs compared to young adults.
+This increase in conservative beliefs as we age may be more extreme for socially conservative beliefs than for fiscally conservate beliefs."}
+
+ggplot(tidy, aes(x = age, y = conservatism_score, color = conservatism_type)) +
+  geom_smooth(se=FALSE, method = "lm")+
+  scale_color_viridis_d() +
+  labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
+       x= "Age", y = "Conservatism Score (higher = more conservative)",
+       color = "Conservatism Type")+
+  theme_minimal()+
+  facet_wrap(~gender)
+```
+
 \endgroup

### 2019-12-02 scripts/manuscript.Rmd
Added citations for all measures in references.bib
Unable to knit, still troubleshooting errors

@@
 
-```{r figure2, fig.cap= "Generally, older adults reported stronger socially and fiscally conservative beliefs compared to young adults.
-This increase in conservative beliefs as we age may be more extreme for socially conservative beliefs than for fiscally conservate beliefs."}
-
-ggplot(tidy, aes(x = age, y = conservatism_score, color = conservatism_type)) +
-  geom_smooth(se=FALSE, method = "lm")+
-  scale_color_viridis_d() +
-  labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
-       x= "Age", y = "Conservatism Score (higher = more conservative)",
-       color = "Conservatism Type")+
-  theme_minimal()+
-  facet_wrap(~gender)
 ```

### 2019-12-07 scripts/manuscript.tex
Updated References

--- 2019-11-19 scripts/manuscript.tex
@@
   \title{Personality and political beliefs across the lifespan}
-    \author{Sarah Dimakis\textsuperscript{1}, Meghan Siritzky\textsuperscript{1}, \&
-Jamie Yellowtail\textsuperscript{1}}
+    \author{Sarah Dimakis\textsuperscript{1}, Meghan Siritzky\textsuperscript{1}, \& Jamie Yellowtail\textsuperscript{1}}
     \date{}
@@
 
-\authornote{This project was completed as part of the EDLD
-Introduction to Data Science class at the University of Oregon.
+\authornote{This project was completed as part of the EDLD Introduction to Data Science class at the University of Oregon.
 
-Correspondence concerning this article should be addressed to Sarah
-Dimakis, University of Oregon, Eugene, OR. E-mail:
-\href{mailto:sdimakis@uoregon.edu}{\nolinkurl{sdimakis@uoregon.edu}}}
+Correspondence concerning this article should be addressed to Sarah Dimakis, University of Oregon, Eugene, OR. E-mail: \href{mailto:sdimakis@uoregon.edu}{\nolinkurl{sdimakis@uoregon.edu}}}
 
 \abstract{
-Someone should write an abstract
+Here is where we will write our abstract.
 
@@
 
-\section{Methods}\label{methods}
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:table1}Mean Personality Trait Scores by Social Conservatism Score}
+\begin{tabular}{llllll}
+\toprule
+ & \multicolumn{5}{c}{Social Conservatism Score} \\
+\cmidrule(r){2-6}
+personality\_trait & \multicolumn{1}{c}{[0-19]} & \multicolumn{1}{c}{[20-39]} & \multicolumn{1}{c}{[40-59]} & \multicolumn{1}{c}{[60-79]} & \multicolumn{1}{c}{[80-100]}\\
+\midrule
+Agreeableness & 4.67 & 5.20 & 4.88 & 5.76 & 5.90\\
+Conscientiousness & 5.37 & 5.44 & 5.32 & 5.84 & 6.03\\
+Emotional stability & 4.07 & 4.38 & 4.82 & 5.50 & 5.57\\
+Extraversion & 2.73 & 3.16 & 3.57 & 3.90 & 3.72\\
+Openness to experiences & 4.93 & 5.40 & 5.43 & 5.25 & 5.12\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Personality trait scores reported on a 1-7 scale.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
 
-We report how we determined our sample size, all data exclusions (if
-any), all manipulations, and all measures in the study.
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:table2}Mean Personality Trait Scores by Economic Conservatism Score}
+\begin{tabular}{llllll}
+\toprule
+ & \multicolumn{5}{c}{Economic Conservatism Score} \\
+\cmidrule(r){2-6}
+personality\_trait & \multicolumn{1}{c}{[0-19]} & \multicolumn{1}{c}{[20-39]} & \multicolumn{1}{c}{[40-59]} & \multicolumn{1}{c}{[60-79]} & \multicolumn{1}{c}{[80-100]}\\
+\midrule
+Agreeableness & 6.14 & 5.21 & 5.29 & 5.40 & 5.43\\
+Conscientiousness & 5.50 & 5.31 & 5.60 & 5.77 & 6.00\\
+Emotional stability & 4.29 & 4.67 & 5.09 & 4.85 & 5.62\\
+Extraversion & 2.79 & 3.67 & 3.61 & 3.42 & 3.50\\
+Openness to experiences & 6.43 & 5.44 & 5.12 & 5.05 & 5.21\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Personality trait scores reported on a 1-7 scale.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
 
-\subsection{Participants}\label{participants}
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:linearmodels_conservatism_ocean_tables}Regression Table Predicting Social Conservatism From Big-Five Personality Traits.}
+\begin{tabular}{lllll}
+\toprule
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(125)$} & \multicolumn{1}{c}{$p$}\\
+\midrule
+Intercept & 25.82 & $[0.07$, $51.58]$ & 1.98 & .049\\
+Openness to experiences & -3.73 & $[-7.50$, $0.04]$ & -1.96 & .052\\
+Conscientiousness & 0.07 & $[-3.98$, $4.11]$ & 0.03 & .974\\
+Extraversion & 1.56 & $[-1.42$, $4.55]$ & 1.04 & .302\\
+Agreeableness & 3.93 & $[0.69$, $7.17]$ & 2.40 & .018\\
+Emotional stability & 4.30 & $[0.70$, $7.91]$ & 2.37 & .020\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Residual standard error: 25.13 on 125 degrees of freedom.
+Multiple R-squared: 0.168, Adjusted R-squared: 0.135. F(5, 125): 5.051, p-value: 0.0003.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
 
-\subsection{Material}\label{material}
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:linearmodels_conservatism_ocean_tables}Regression Table Predicting Economic Conservatism From Big-Five Personality Traits.}
+\begin{tabular}{lllll}
+\toprule
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(125)$} & \multicolumn{1}{c}{$p$}\\
+\midrule
+Intercept & 56.54 & $[34.71$, $78.37]$ & 5.13 & < .001\\
+Openness to experiences & -3.79 & $[-6.98$, $-0.59]$ & -2.35 & .021\\
+Conscientiousness & 1.78 & $[-1.65$, $5.20]$ & 1.03 & .307\\
+Extraversion & 0.61 & $[-1.92$, $3.14]$ & 0.48 & .632\\
+Agreeableness & -1.13 & $[-3.88$, $1.61]$ & -0.82 & .415\\
+Emotional stability & 2.34 & $[-0.71$, $5.39]$ & 1.52 & .131\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Residual standard error: 21.3 on 125 degrees of freedom. Multiple R-squared: 0.081, Adjusted R-squared: 0.044. F(5, 125): 2.207, p-value: 0.058.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
 
-\subsection{Procedure}\label{procedure}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
-\subsection{Data analysis}\label{data-analysis}
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
-We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
-\emph{dplyr} (Version 0.8.3; Wickham, François, Henry, \& Müller, 2019),
-\emph{forcats} (Version 0.4.0; Wickham, 2019a), \emph{ggplot2} (Version
-3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017),
-\emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{purrr}
-(Version 0.3.3; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1;
-Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; C.-h.
-Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0;
-Wickham, 2019b), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019),
-\emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and
-\emph{tidyverse} (Version 1.2.1; Wickham, 2017) for all our analyses.
+\hypertarget{material}{%
+\subsection{Material}\label{material}}
 
-\section{Results}\label{results}
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
-\section{Discussion}\label{discussion}
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
+
+We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{forcats} (Version 0.4.0; Wickham, 2019a), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019b), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+In order to understand the relation between conservatism and personality, we first looked at Big Five personality trait (Openness to Experience, Conscientiousness, Extraversion, Agreeableness, and Emotional Stability) scores across the spectrum of Social Conservatism (Table 1) and Economic Conservatism (Table 2) scores.
+
+To see whether there were significant relations between Social Conservatism and the Big Five, we then ran a multiple regression predicting Social Conservatism from the Big Five personality traits.
+A significant regression equation was found (\emph{F}(5, 125) = 5.051, \emph{p} \textless{} .001), with an adjusted \(R^2\) of 0.135 (Table 2).
+Thus, personality traits taken together explained 13.48\% of variance in Social Conservatism scores.
+Participants' predicted Social Conservatism scores were equal to 25.82 - 3.73(Openness to Experience) + 0.07(Conscientiousness) + 1.56(Extraversion) + 3.93(Agreeableness) + 4.30(Emotional Stability).
+Agreeableness and Emotional Stability were significant predictors of Social Conservatism.
+
+To see whether there were significant relations between Economic Conservatism and the Big Five, we then ran a multiple regression predicting Economic Conservatism from the Big Five personality traits.
+No significant regression equation was found (\emph{F}(5, 125) = 2.207, \emph{p} = .058) (Table 3).
+Thus, personality traits taken together did not significantly explain variance in Economic Conservatism scores.
+However, Openness to Experience was a significant predictor of Economic Conservatism.
+
+To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be r = 0.65.
+Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits.
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 
-\section{References}\label{references}
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begin{verbatim}
+## Warning in readLines(file): incomplete final line found on 'r-
+## references.bib'
+\end{verbatim}
 
 \begingroup
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-R-papaja}{}
-Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with
-R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\hypertarget{ref-R-rio}{}
-Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018).
-\emph{Rio: A swiss-army knife for data file i/o}.
+\leavevmode\hypertarget{ref-R-rio}{}%
+Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.
 
-\hypertarget{ref-R-purrr}{}
-Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
-tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+\leavevmode\hypertarget{ref-R-janitor}{}%
+Firke, S. (2019). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
 
-\hypertarget{ref-R-here}{}
-Müller, K. (2017). \emph{Here: A simpler way to find your files}.
-Retrieved from \url{https://CRAN.R-project.org/package=here}
+\leavevmode\hypertarget{ref-R-viridis}{}%
+Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}
 
-\hypertarget{ref-R-tibble}{}
-Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
-Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+\leavevmode\hypertarget{ref-R-viridisLite}{}%
+Garnier, S. (2018b). \emph{ViridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}
 
-\hypertarget{ref-R-base}{}
-R Core Team. (2019). \emph{R: A language and environment for statistical
-computing}. Vienna, Austria: R Foundation for Statistical Computing.
-Retrieved from \url{https://www.R-project.org/}
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
 
-\hypertarget{ref-R-ggplot2}{}
-Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
-Springer-Verlag New York. Retrieved from
-\url{https://ggplot2.tidyverse.org}
+\leavevmode\hypertarget{ref-R-here}{}%
+Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}
 
-\hypertarget{ref-R-tidyverse}{}
-Wickham, H. (2017). \emph{Tidyverse: Easily install and load the
-'tidyverse'}. Retrieved from
-\url{https://CRAN.R-project.org/package=tidyverse}
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
-\hypertarget{ref-R-forcats}{}
-Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical
-variables (factors)}. Retrieved from
-\url{https://CRAN.R-project.org/package=forcats}
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
-\hypertarget{ref-R-stringr}{}
-Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for
-common string operations}. Retrieved from
-\url{https://CRAN.R-project.org/package=stringr}
+\leavevmode\hypertarget{ref-R-psych}{}%
+Revelle, W.
+(2018).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
 
-\hypertarget{ref-R-tidyr}{}
-Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}.
-Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
 
-\hypertarget{ref-R-dplyr}{}
-Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr:
-A grammar of data manipulation}. Retrieved from
-\url{https://CRAN.R-project.org/package=dplyr}
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}
 
-\hypertarget{ref-R-readr}{}
-Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read
-rectangular text data}. Retrieved from
-\url{https://CRAN.R-project.org/package=readr}
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
+
+Call:corr.test(x = untidy\(economic_conservatism, y = untidy\)social\_conservatism)
+Correlation matrix
+{[}1{]} 0.65
+Sample Size
+{[}1{]} 131
+Probability values adjusted for multiple tests.
+{[}1{]} 0
+
+To see confidence intervals of the correlations, print with the short=FALSE option
+
+\begin{lltable}
+
+\tiny{
+\begin{longtable}{llllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:correlations}Correlation Matrix for Conservatism and Big Five Personality Traits}\\
+\toprule
+ & \multicolumn{1}{c}{Economic conservatism} & \multicolumn{1}{c}{Social conservatism} & \multicolumn{1}{c}{Agreeableness} & \multicolumn{1}{c}{Conscientiousness} & \multicolumn{1}{c}{Openness to experiences} & \multicolumn{1}{c}{Extraversion} & \multicolumn{1}{c}{Emotional stability}\\
+\midrule
+Economic conservatism & 1 &  &  &  &  &  & \\
+Social conservatism & 0.65 & 1 &  &  &  &  & \\
+Agreeableness & -0.02 & 0.29 & 1 &  &  &  & \\
+Conscientiousness & 0.14 & 0.18 & 0.28 & 1 &  &  & \\
+Openness to experiences & -0.15 & -0.02 & 0.2 & 0.18 & 1 &  & \\
+Extraversion & 0.02 & 0.17 & 0.2 & 0.12 & 0.44 & 1 & \\
+Emotional stability & 0.16 & 0.33 & 0.35 & 0.54 & 0.28 & 0.42 & 1\\
+\bottomrule
+\end{longtable}
+}
+\end{lltable}
+
+\includegraphics{manuscript_files/figure-latex/correlations-1.pdf}
+
+\includegraphics{manuscript_files/figure-latex/figure1-1.pdf}
+
+```
 

### 2019-12-08 scripts/manuscript.Rmd
Materials Section
Primary measures: TIPI and SECS

@@
 
+**_Personality_** To assess participant personality traits, respondents completed the Ten Item Personality Inventory [@gosling2003very].
+Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g.
+“Extraverted, enthusiastic”; “Critical, quarrelsome”).
+Respondents rated each statement on a 7-point likert scale (1 = Strongly Disagree to 7 = Strongly Agree).
+Responses were coded such that higher values reflected greater identification with the personality trait .
+
+**_Social and Economic Conservatism_** To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale [@everett201312].
+Participants were asked to indicate the extent to which they feel positively or negatively about twelve distinct issues (eg.
+Abortion; Patriotism).
+Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity).
+Responses were coded such that higher values reflected greater levels of conservatism.
+
 ## Procedure

### 2019-12-08 scripts/manuscript.tex
Materials Section
Primary measures: TIPI and SECS

@@
 
+\textbf{\emph{Personality}} To assess participant personality traits, respondents completed the Ten Item Personality Inventory (Gosling, Rentfrow, \& Swann Jr, 2003).
+Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g.
+\enquote{Extraverted, enthusiastic}; \enquote{Critical, quarrelsome}).
+Respondents rated each statement on a 7-point likert scale (1 = Strongly Disagree to 7 = Strongly Agree).
+Responses were coded such that higher values reflected greater identification with the personality trait .
+
+\textbf{\emph{Social and Economic Conservatism}} To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale (Everett, 2013).
+Participants were asked to indicate the extent to which they feel positively or negatively about twelve distinct issues (eg.
+Abortion; Patriotism).
+Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity).
+Responses were coded such that higher values reflected greater levels of conservatism.
+
 \hypertarget{procedure}{%
@@
 
+\leavevmode\hypertarget{ref-everett201312}{}%
+Everett, J. A. (2013). The 12 item social and economic conservatism scale (secs). \emph{PloS One}, \emph{8}(12), e82131.
+
 \leavevmode\hypertarget{ref-R-janitor}{}%
@@
 Garnier, S. (2018b). \emph{ViridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}
+
+\leavevmode\hypertarget{ref-gosling2003very}{}%
+Gosling, S. D., Rentfrow, P. J., \& Swann Jr, W. B. (2003). A very brief measure of the big-five personality domains. \emph{Journal of Research in Personality}, \emph{37}(6), 504--528.
 

### 2019-12-10 scripts/manuscript.tex
Participants and Procedure

@@
 
+Two hundred US adults were recruited through Amazon Mechanical Turk to participate in the \enquote{Psychology and society survey} (Dimakis \& Mauro, 2019).
+Of the two hundred survey takers, 66 were excluded from data analysis \emph{(N =131)} due to failing the included attention checks.
+The gender of participants in this study was 54.2\% female and 45.8\% male.
+Age of participants ranged from 20 to 68 years old \emph{(M = 40.55, SD = 11.98)}.
+Participants that chose to self-identify their ethnicity included 77.1\% Caucasian or White, 7.6\% African American or Black, 5.3\% Asian, 6.1\% Hispanic or Latino, .8\% Native American, and 3.1\% identified their ethnicity as other.
+Political affiliation of respondents include 45.0\% Democrat, 23.7\% Republican, 22.1\% no party, 5.3\% other, 2.3\% Green Party, and 1.5\% Libertarian.
+Participants were compensated \$1.50 for taking the survey, which took on average 11 minutes and 19 seconds to complete.
+
 \hypertarget{material}{%
@@
 \textbf{\emph{Social and Economic Conservatism}} To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale (Everett, 2013).
-Participants were asked to indicate the extent to which they feel positively or negatively about twelve distinct issues (eg.
-Abortion; Patriotism).
+Participants were asked to indicate the extent to which they feel positively or negatively about seven social issues and five economic issues (eg.
+Abortion; Fiscal Responsibility).
 Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity).
@@
 
+\textbf{\emph{Additional Measures}} Researchers created video manipulations to induce different emotions: clips from \emph{The Shining} and \emph{The Blair Witch Project} were used to induce fear, clips from \emph{Seven} and \emph{Schindler's List} were used to induce anger, and clips from \emph{Blue} were used to induce no emotion.
+Researchers also created a statement on the prevalence of homelessness with corresponding policy statements varying in complexity and politics.
+Additional measures used in the study include the PANAS Affect Scale (Watson, Clark, \& Tellegen, 1988), the 18-Point Need for Cognition Scale {[}cacioppo1984efficient{]}, and the 10-Point Emotion Regulation Scale {[}gross2003individual{]}.
+
 \hypertarget{procedure}{%
 \subsection{Procedure}\label{procedure}}
+
+Participants accessed the \enquote{Psychology and society survey} through the online Amazon Mechanical Turk website.
+Once informed consent was confirmed, participants were randomly assigned to watch a video that would induce fear, anger, or no emotion.
+After watching the video, each participant was presented with information describing homelessness in America.
+Participants were then randomly assigned to read a policy statement addressing homelessness that was either simple or complex, liberal or conservative, and were then asked to answer questions measuring their beliefs about the policy.
+Additional measures followed including the Social and Economic Conservatism Scale, Ten Item Personality Scale, PANAS Affect Scale, Need for Cognition Scale, and the Emotional Regulation Scale.
+Participants concluded the study by providing demographic information.
 
@@
 
+\leavevmode\hypertarget{ref-Dimakis_Mauro_2019}{}%
+Dimakis, S., \& Mauro, R. (2019). Unpublished dataset, emotions and political beliefs, study 2.
+
 \leavevmode\hypertarget{ref-everett201312}{}%
@@
 Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
+\leavevmode\hypertarget{ref-watson1988development}{}%
+Watson, D., Clark, L.
+A., \& Tellegen, A.
+(1988).
+Development and validation of brief measures of positive and negative affect: The panas scales.
+\emph{Journal of Personality and Social Psychology}, \emph{54}(6), 1063.
 
@@
 
-\includegraphics{manuscript_files/figure-latex/correlations-1.pdf}
+\includegraphics{manuscript_files/figure-latex/figure1-1.pdf}
 
-\includegraphics{manuscript_files/figure-latex/figure1-1.pdf}
+\includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
 

### 2019-12-10 scripts/manuscript.tex
Merge conflicts

--- 2019-12-07 scripts/manuscript.tex
@@
   \title{Personality and political beliefs across the lifespan}
-    \author{Sarah Dimakis\textsuperscript{1}, Meghan Siritzky\textsuperscript{1}, \& Jamie Yellowtail\textsuperscript{1}}
+    \author{Sarah Dimakis\textsuperscript{1}, Meghan Siritzky\textsuperscript{1}, \&
+Jamie Yellowtail\textsuperscript{1}}
     \date{}
@@
 
-\authornote{This project was completed as part of the EDLD Introduction to Data Science class at the University of Oregon.
+\authornote{This project was completed as part of the EDLD
+Introduction to Data Science class at the University of Oregon.
 
-Correspondence concerning this article should be addressed to Sarah Dimakis, University of Oregon, Eugene, OR. E-mail: \href{mailto:sdimakis@uoregon.edu}{\nolinkurl{sdimakis@uoregon.edu}}}
+Correspondence concerning this article should be addressed to Sarah
+Dimakis, University of Oregon, Eugene, OR. E-mail:
+\href{mailto:sdimakis@uoregon.edu}{\nolinkurl{sdimakis@uoregon.edu}}}
 
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\section{Methods}\label{methods}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
-\hypertarget{material}{%
-\subsection{Material}\label{material}}
+\subsection{Material}\label{material}
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\subsection{Procedure}\label{procedure}
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+\subsection{Data analysis}\label{data-analysis}
 
-We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{forcats} (Version 0.4.0; Wickham, 2019a), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019b), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
+We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
+\emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham,
+François, Henry, \& Müller, 2019), \emph{forcats} (Version 0.4.0;
+Wickham, 2019a), \emph{ggplot2} (Version 3.2.1; Wickham, 2016),
+\emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0;
+Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja}
+(Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12;
+Revelle, 2018), \emph{purrr} (Version 0.3.3; Henry \& Wickham, 2019),
+\emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018),
+\emph{rio} (Version 0.5.16; C.-h. Chan, Chan, Leeper, \& Becker, 2018),
+\emph{stringr} (Version 1.4.0; Wickham, 2019b), \emph{tibble} (Version
+2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \&
+Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017),
+\emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and
+\emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
-In order to understand the relation between conservatism and personality, we first looked at Big Five personality trait (Openness to Experience, Conscientiousness, Extraversion, Agreeableness, and Emotional Stability) scores across the spectrum of Social Conservatism (Table 1) and Economic Conservatism (Table 2) scores.
+In order to understand the relation between conservatism and
+personality, we first looked at Big Five personality trait (Openness to
+Experience, Conscientiousness, Extraversion, Agreeableness, and
+Emotional Stability) scores across the spectrum of Social Conservatism
+(Table 1) and Economic Conservatism (Table 2) scores.
 
-To see whether there were significant relations between Social Conservatism and the Big Five, we then ran a multiple regression predicting Social Conservatism from the Big Five personality traits.
-A significant regression equation was found (\emph{F}(5, 125) = 5.051, \emph{p} \textless{} .001), with an adjusted \(R^2\) of 0.135 (Table 2).
-Thus, personality traits taken together explained 13.48\% of variance in Social Conservatism scores.
-Participants' predicted Social Conservatism scores were equal to 25.82 - 3.73(Openness to Experience) + 0.07(Conscientiousness) + 1.56(Extraversion) + 3.93(Agreeableness) + 4.30(Emotional Stability).
-Agreeableness and Emotional Stability were significant predictors of Social Conservatism.
+To see whether there were significant relations between Social
+Conservatism and the Big Five, we then ran a multiple regression
+predicting Social Conservatism from the Big Five personality traits. A
+significant regression equation was found (\emph{F}(5, 125) = 5.051,
+\emph{p} \textless{} .001), with an adjusted \(R^2\) of 0.135 (Table 2).
+Thus, personality traits taken together explained 13.48\% of variance in
+Social Conservatism scores. Participants' predicted Social Conservatism
+scores were equal to 25.82 - 3.73(Openness to Experience) +
+0.07(Conscientiousness) + 1.56(Extraversion) + 3.93(Agreeableness) +
+4.30(Emotional Stability). Agreeableness and Emotional Stability were
+significant predictors of Social Conservatism.
 
-To see whether there were significant relations between Economic Conservatism and the Big Five, we then ran a multiple regression predicting Economic Conservatism from the Big Five personality traits.
-No significant regression equation was found (\emph{F}(5, 125) = 2.207, \emph{p} = .058) (Table 3).
-Thus, personality traits taken together did not significantly explain variance in Economic Conservatism scores.
-However, Openness to Experience was a significant predictor of Economic Conservatism.
+To see whether there were significant relations between Economic
+Conservatism and the Big Five, we then ran a multiple regression
+predicting Economic Conservatism from the Big Five personality traits.
+No significant regression equation was found (\emph{F}(5, 125) = 2.207,
+\emph{p} = .058) (Table 3). Thus, personality traits taken together did
+not significantly explain variance in Economic Conservatism scores.
+However, Openness to Experience was a significant predictor of Economic
+Conservatism.
 
-To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be r = 0.65.
-Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits.
+To better understand the relation between social and economic
+conservatism, we examined the correlation between social and economic
+conservatism scores, and found it to be r = 0.65. Neither social nor
+economic extraversion were strongly correlated with any of the Big Five
+personality traits.
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Discussion}\label{discussion}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
@@
 \begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+\hypertarget{ref-R-papaja}{}
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with
+R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\hypertarget{ref-R-rio}{}%
-Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.
+\hypertarget{ref-R-rio}{}
+Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018).
+\emph{Rio: A swiss-army knife for data file i/o}.
 
-\leavevmode\hypertarget{ref-R-janitor}{}%
-Firke, S. (2019). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
+\hypertarget{ref-R-janitor}{}
+Firke, S. (2019). \emph{Janitor: Simple tools for examining and cleaning
+dirty data}. Retrieved from
+\url{https://CRAN.R-project.org/package=janitor}
 
-\leavevmode\hypertarget{ref-R-viridis}{}%
-Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}
+\hypertarget{ref-R-viridis}{}
+Garnier, S. (2018a). \emph{Viridis: Default color maps from
+'matplotlib'}. Retrieved from
+\url{https://CRAN.R-project.org/package=viridis}
 
-\leavevmode\hypertarget{ref-R-viridisLite}{}%
-Garnier, S. (2018b). \emph{ViridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}
+\hypertarget{ref-R-viridisLite}{}
+Garnier, S. (2018b). \emph{ViridisLite: Default color maps from
+'matplotlib' (lite version)}. Retrieved from
+\url{https://CRAN.R-project.org/package=viridisLite}
 
-\leavevmode\hypertarget{ref-R-purrr}{}%
-Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+\hypertarget{ref-R-purrr}{}
+Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
+tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
 
-\leavevmode\hypertarget{ref-R-here}{}%
-Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}
+\hypertarget{ref-R-here}{}
+Müller, K. (2017). \emph{Here: A simpler way to find your files}.
+Retrieved from \url{https://CRAN.R-project.org/package=here}
 
-\leavevmode\hypertarget{ref-R-tibble}{}%
-Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+\hypertarget{ref-R-tibble}{}
+Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
+Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+\hypertarget{ref-R-base}{}
+R Core Team. (2019). \emph{R: A language and environment for statistical
+computing}. Vienna, Austria: R Foundation for Statistical Computing.
+Retrieved from \url{https://www.R-project.org/}
 
-\leavevmode\hypertarget{ref-R-psych}{}%
-Revelle, W.
-(2018).
-\emph{Psych: Procedures for psychological, psychometric, and personality research}.
-Evanston, Illinois: Northwestern University.
-Retrieved from \url{https://CRAN.R-project.org/package=psych}
+\hypertarget{ref-R-psych}{}
+Revelle, W. (2018). \emph{Psych: Procedures for psychological,
+psychometric, and personality research}. Evanston, Illinois:
+Northwestern University. Retrieved from
+\url{https://CRAN.R-project.org/package=psych}
 
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
-Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+\hypertarget{ref-R-ggplot2}{}
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
+Springer-Verlag New York. Retrieved from
+\url{https://ggplot2.tidyverse.org}
 
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
-Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}
+\hypertarget{ref-R-tidyverse}{}
+Wickham, H. (2017). \emph{Tidyverse: Easily install and load the
+'tidyverse'}. Retrieved from
+\url{https://CRAN.R-project.org/package=tidyverse}
 
-\leavevmode\hypertarget{ref-R-forcats}{}%
-Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+\hypertarget{ref-R-forcats}{}
+Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical
+variables (factors)}. Retrieved from
+\url{https://CRAN.R-project.org/package=forcats}
 
-\leavevmode\hypertarget{ref-R-stringr}{}%
-Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+\hypertarget{ref-R-stringr}{}
+Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for
+common string operations}. Retrieved from
+\url{https://CRAN.R-project.org/package=stringr}
 
-\leavevmode\hypertarget{ref-R-dplyr}{}%
-Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+\hypertarget{ref-R-tidyr}{}
+Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}.
+Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
 
-\leavevmode\hypertarget{ref-R-tidyr}{}%
-Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+\hypertarget{ref-R-dplyr}{}
+Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr:
+A grammar of data manipulation}. Retrieved from
+\url{https://CRAN.R-project.org/package=dplyr}
 
-\leavevmode\hypertarget{ref-R-readr}{}%
-Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+\hypertarget{ref-R-readr}{}
+Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read
+rectangular text data}. Retrieved from
+\url{https://CRAN.R-project.org/package=readr}
 
-\leavevmode\hypertarget{ref-R-knitr}{}%
-Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
+\hypertarget{ref-R-knitr}{}
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.).
+Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from
+\url{https://yihui.name/knitr/}
 
-Call:corr.test(x = untidy\(economic_conservatism, y = untidy\)social\_conservatism)
-Correlation matrix
-{[}1{]} 0.65
-Sample Size
-{[}1{]} 131
-Probability values adjusted for multiple tests.
-{[}1{]} 0
+Call:corr.test(x =
+untidy\(economic_conservatism, y = untidy\)social\_conservatism)
+Correlation matrix {[}1{]} 0.65 Sample Size {[}1{]} 131 Probability
+values adjusted for multiple tests. {[}1{]} 0
 
-To see confidence intervals of the correlations, print with the short=FALSE option
+To see confidence intervals of the correlations, print with the
+short=FALSE option
 
@@
 
+\begin{figure}
+\centering
 \includegraphics{manuscript_files/figure-latex/correlations-1.pdf}
+\caption{}
+\end{figure}
 

### 2019-12-10 scripts/manuscript.Rmd

@@
 
+```{r}
+age_mean <- mean(data$age, na.rm = TRUE)
+age_sd <- sd(data$age, na.rm = TRUE)
+```
+
 # Methods
@@
 ## Participants
+
+Two hundred US adults were recruited through Amazon Mechanical Turk to participate in the “Psychology and society survey” [@Dimakis_Mauro_2019].
+Of the two hundred survey takers, 66 were excluded from data analysis _(N =131)_ due to failing the included  attention checks.
+The gender of participants in this study was 54.2% female and 45.8% male.
+Age of participants ranged from 20 to 68 years old _(M = `r age_mean`, SD = `r age_sd`)_.
+Participants that chose to self-identify their ethnicity included  77.1% Caucasian or White, 7.6% African American or Black, 5.3% Asian, 6.1% Hispanic or Latino, .8% Native American, and 3.1% identified their ethnicity as other.
+Political affiliation of respondents include 45.0% Democrat, 23.7% Republican, 22.1% no party, 5.3% other, 2.3% Green Party, and 1.5% Libertarian.
+Participants were compensated $1.50 for taking the survey, which took on average 11 minutes and 19 seconds to complete.
 
@@
 **_Social and Economic Conservatism_** To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale [@everett201312].
-Participants were asked to indicate the extent to which they feel positively or negatively about twelve distinct issues (eg.
-Abortion; Patriotism).
+Participants were asked to indicate the extent to which they feel positively or negatively about seven social issues and five economic issues (eg.
+Abortion; Fiscal Responsibility).
 Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity).
@@
 
+**_Additional Measures_** Researchers created video manipulations to induce different emotions: clips from _The Shining_ and _The Blair Witch Project_ were used to induce fear, clips from _Seven_ and _Schindler’s List_ were used to induce anger, and clips from _Blue_ were used to induce no emotion.
+Researchers also created a statement on the prevalence of homelessness with corresponding policy statements varying in complexity and politics.
+  Additional measures used in the study include the PANAS Affect Scale [@watson1988development], the 18-Point Need for Cognition Scale [cacioppo1984efficient], and the 10-Point Emotion Regulation Scale [gross2003individual].
+
 ## Procedure
+
+Participants accessed the “Psychology and society survey” through the online Amazon Mechanical Turk website.
+Once informed consent was confirmed, participants were randomly assigned to watch a video that would induce fear, anger, or no emotion.
+After watching the video, each participant was presented with information describing homelessness in America.
+Participants were then randomly assigned to read a policy statement addressing homelessness that was either simple or complex, liberal or conservative, and were then asked to answer questions measuring their beliefs about the policy.
+Additional measures followed including the Social and Economic Conservatism Scale, Ten Item Personality Scale, PANAS Affect Scale, Need for Cognition Scale, and the Emotional Regulation Scale.
+Participants concluded the study by providing demographic information.
 
@@
 
+```
+
+```{r figure1, fig.cap=""}
 heatmap(cor_conservatism_ocean,
@@
 
-```{r figure1, fig.cap= ""}
+```{r figure2, fig.cap= ""}
 ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +

### 2019-12-10 scripts/manuscript.Rmd
edits to method results

--- 2019-12-02 scripts/manuscript.Rmd
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 #Aggregating the social and economic conservationism scale (SECs) using scoreItems from the psych package and mutate from dplyr
-items <- c("Q3_1", "Q3_2","Q3_3","Q3_4","Q3_5","Q3_6","Q3_7","Q3_8","Q3_9","Q3_10","Q3_11","Q3_12" )
+items <- c("Q3_1", "Q3_2","Q3_3","Q3_4","Q3_5","Q3_6","Q3_7","Q3_8","Q3_9","Q3_10","Q3_11","Q3_12")
 
@@
 data <- data %>% 
-  select(ResponseId, Q7, Q8, Q9, Q10, Q11,
+  select(ResponseId, Q7, Q8, Q9, Q10, Q11, Duration__in_seconds_,
          SEC_economic_conservatism, SEC_social_conservatism,
@@
                values_to = "personality_score") %>% 
-  mutate(personality_trait = recode(personality_trait, `agreeableness` = "Agreeableness",
+  mutate(personality_trait = 
+           recode(personality_trait,
+                  `agreeableness` = "Agreeableness",
                   `conscientiousness` = "Conscientiousness",
@@
 ```{r table1, echo = FALSE, results = "asis"}
+#this table is of the mean personality trait scores by social conservatism scores
 tidy_table_sc <- tidy %>% 
@@
 
+```{r, include = FALSE}
+#Age statistics
+mean_age <- mean(as.numeric(data$age)) %>% round(2)
+sd_age <- sd(as.numeric(data$age)) %>% round(2)
+r1_age <- range(as.numeric(data$age))[1]
+r2_age <- range(as.numeric(data$age))[2]
+
+#Number of participants
+n <- nrow(data)
+
+#Ethnicity
+#I'm creating a function that will spit out the percentage of people with a given ethnicity, including a % sign
+percent_ethn <- function(pos){
+  paste(((table(data$ethnicity)[[pos]]/n) *100) %>% round(1), "%", sep = "")}
+black <-percent_ethn(1)
+asian <- percent_ethn(2)
+white <- percent_ethn(3)
+hispanic <- percent_ethn(4)
+native <- percent_ethn(5)
+other <- percent_ethn(6)
+
+#Gender
+percent_gen <- function(pos){
+  paste(((table(data$gender)[[pos]]/n) *100) %>% round(1), "%", sep = "")}
+female <- percent_gen(1)
+male <- percent_gen(2)
+
+#politicial affiliation
+percent_pa <- function(pos){
+  paste(((table(data$political_affiliation)[[pos]]/n) *100) %>% round(1), "%", sep = "")}
+democrat <- percent_pa(1)
+republican <- percent_pa(6)
+no_party <- percent_pa(4)
+other_n <- table(data$political_affiliation)[[2]]+
+  table(data$political_affiliation)[[3]]+
+  table(data$political_affiliation)[[5]]
+other <- paste(((other_n/n) *100) %>% round(1), "%", sep = "")
+
+#Duration
+data <- data %>% 
+  mutate(duration_in_seconds = as.numeric(duration_in_seconds))
+duration_m <- mean(data$duration_in_seconds)/60
+duration_sd <- sd(data$duration_in_seconds)/60
+```
 ## Participants
+
+Two-hundred U.S.
+adults were recruited via Amazon Mechanical Turk to participate in a study listed as "Psychology and society survey." Participants were removed for completing the survey quicker than predetermined time cutoffs or failing to pass attention checks.
+Of the remaining `r n` participants, who were `r r1_age` to `r r2_age` years old (*M* = `r mean_age`, *SD* = `r sd_age`), `r female` identified as female and `r male` identified as male, while `r white` identified as White of Caucasian, `r black` as African American or Black, `r hispanic` as Hispanic or Latinx, `r asian` as Asian or Asian American, `r native` as Native American, and `r other` as "Other." The sample leaned liberal, with `r democrat` affiliated with the Democratic Party, `r republican` affiliated with the Republican Party, `r no_party` affiliated with no party, and `r other` affiliated with the Green Party, Libertarian Party, or another party.
+The participants were compensated $1.50 for completing the survey, which took on average `r duration_m` minutes (*SD* = `r duration_sd`).
 
@@
 
+**Personality.** To assess personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability), respondents completed the Ten Item Personality Inventory [@gosling2003very].
+Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g.
+“Extraverted, enthusiastic”; “Critical, quarrelsome”).
+Respondents rated each statement on a 7-point likert scale (1 = Strongly Disagree to 7 = Strongly Agree).
+Responses were coded such that higher values reflected greater identification with the personality trait.
+
+**Social and Economic Conservatism.** To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale [@everett201312].
+Participants were asked to indicate the extent to which they feel positively or negatively about seven social issues and five economic issues (eg.
+Abortion; Fiscal Responsibility).
+Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity).
+Responses were coded such that higher values reflected greater levels of conservatism.
+
+**Additional Measures.** Incidental affect was induced via video clips [@schaefer2010].
+Clips from _The Shining_ and _The Blair Witch Project_ were used to induce fear, clips from _Seven_ and _Schindler’s List_ were used to induce anger, and clips from _Blue_ were used to induce no emotion.
+Participants also read a speech on the prevalence of homelessness in the United States and a corresponding policy varying in complexity and affiliation.
+
+Participants completed additional measures, including an adjusted PANAS Affect Scale assessing current emotional state [@watson1988development], the 18-Point Need for Cognition Scale assessing need for cognition [@cacioppo1984efficient], the 10-Point Emotion Regulation Questionnaire assessing the use of two emotional regulation strategies, cognitive reappraisal and expressive supression [@gross2003individual], and demographic information, including gender, ethnicity, age, and political orientation and affiliation.
+
 ## Procedure
+
+Participants accessed the survey through the Amazon Mechanical Turk website.
+Once informed consent was confirmed, participants were randomly assigned to watch a video intended to induce primarily fear, anger, or no emotion.
+After watching the video, each participant was presented with information describing the prevalance of homelessness in the United States.
+Participants were then randomly assigned to read a policy statement addressing homelessness that was either simple or complex, and liberal or conservative, and were then asked to answer questions measuring their beliefs about the policy.
+Additional measures followed measuring social and economic conservatism, personality traits, current affective state, neeed for cognition, and emotional regulation.
+Participants concluded the study by providing demographic information.
 
@@
 
-In order to understand the relation between conservatism and personality, we first looked at Big Five personality trait (Openness to Experience, Conscientiousness, Extraversion, Agreeableness, and Emotional Stability) scores across the spectrum of Social Conservatism (Table 1) and Economic Conservatism (Table 2) scores.
+In order to explore relation between conservatism and personality, we created a table of the Big Five personality trait (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability) scores across different levels of social (see Table 1) and economic (see Table 2) conservatism.
 
-To see whether there were significant relations between Social Conservatism and the Big Five, we then ran a multiple regression predicting Social Conservatism from the Big Five personality traits.
-A significant regression equation was found (*F*(5, 125) = 5.051, *p* < .001), with an adjusted $R^2$ of 0.135 (Table 2).
-Thus, personality traits taken together explained 13.48% of variance in Social Conservatism scores.
-Participants' predicted Social Conservatism scores were equal to 25.82 - 3.73(Openness to Experience) + 0.07(Conscientiousness) + 1.56(Extraversion) + 3.93(Agreeableness) + 4.30(Emotional Stability).
-Agreeableness and Emotional Stability were significant predictors of Social Conservatism.
+To see whether there were significant relations between social conservatism and the Big Five traits, we then ran a multiple regression predicting social conservatism from the Big Five personality traits.
+We found that together the personality traits explain about 13.5% of the variance in social conservatism scores, *F*(5, 125) = 5.05, *p* < .001, with an adjusted $R^2$ of .14 (see Table 3).
+We found that agreeablessness, $\beta$ = 3.93, *t*(125) = 2.40, *p* = .018, and emotional stability, $\beta$ = 4.30, *t*(125) = 2.37, *p* = .020, significantly predict social conservatism, such that, controlling for the other personality traits, those who scored higher on agreeableness and emotional stability measures tended to also score higher on the social conservatism measure.
+Additionally, openness to experiences margionally predicted social conservatism, $\beta$ = -3.73, *t*(125) = -1.96, *p* = .052, such that, controlling for other personality traits, those who scored higher on conservatism tended to score lower on the openness to experience measure.
 
-To see whether there were significant relations between Economic Conservatism and the Big Five, we then ran a multiple regression predicting Economic Conservatism from the Big Five personality traits.
-No significant regression equation was found (*F*(5, 125) = 2.207, *p* = .058) (Table 3).
-Thus, personality traits taken together did not significantly explain variance in Economic Conservatism scores.
-However, Openness to Experience was a significant predictor of Economic Conservatism.
+To see whether there were significant relations between economic conservatism and the Big Five traits, we then ran a multiple regression predicting economic conservatism from the Big Five personality traits.
+The personality traits taken together did not significantly explain variance in economic conservatism scores, *F*(5, 125) = 2.21, *p* = .058 (see Table 4).
+However, openness to experience was a significant predictor of economic conservatism, $\beta$ = -3.79, *t*(125) = -2.35, *p* = .021, such that, controlling for other personality traits, those who scored high on economic conservatism subscale tended to score lower on the openness to experiences measure.
 
-To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be r = 0.65.
-Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits.
+To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be *r* = .65.
+Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits (see Figure 1).
 
@@
 untidy_cor <- untidy %>% 
-  select(-c(1:6)) %>% 
+  select(-c(1:7)) %>% 
   rename('Social conservatism' = 'social_conservatism',
@@
 
+```
+
+```{r figure1, fig.cap="A correlation heatmap demonstrating the correlations between the Big Five personality traits and social and economic conservatism."}
 heatmap(cor_conservatism_ocean,
@@
 
-```{r figure1, fig.cap= ""}
-ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +
+```{r figure2, fig.cap= "We found a significant positive relation between emotional stability and social conservatism, a positive relation between agreeableness and social conservatism, and a negative relation between openness to experiences and economic conservatism.", fig.height = 10, fig.width = 8}
+ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = conservatism_type)) +
   geom_smooth(se=FALSE, method = "lm")+
   labs(title = "Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
-       x= "How strongly participants identify with the personality trait", y = "Conservatism", 
-       color = "Personality Trait")+
+       x= "How strongly participants identify with the personality trait", y = "Conservatism score", 
+       color = "Conservatism type")+
   theme_minimal()+
   scale_color_viridis_d() +
-  facet_wrap(~conservatism_type)
+  facet_wrap(~personality_trait, ncol = 1)
 ```

### 2019-12-10 scripts/manuscript.tex
edits to method results

@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
 
@@
 
+Two-hundred U.S. adults were recruited via Amazon Mechanical Turk to
+participate in a study listed as \enquote{Psychology and society
+survey.} Participants were removed for completing the survey quicker
+than predetermined time cutoffs or failing to pass attention checks. Of
+the remaining 131 participants, who were 20 to 68 years old (\emph{M} =
+40.55, \emph{SD} = 11.98), 54.2\% identified as female and 45.8\%
+identified as male, while 77.1\% identified as White of Caucasian, 7.6\%
+as African American or Black, 6.1\% as Hispanic or Latinx, 5.3\% as
+Asian or Asian American, 0.8\% as Native American, and 9.2\% as
+\enquote{Other.} The sample leaned liberal, with 45\% affiliated with
+the Democratic Party, 23.7\% affiliated with the Republican Party,
+22.1\% affiliated with no party, and 9.2\% affiliated with the Green
+Party, Libertarian Party, or another party. The participants were
+compensated \$1.50 for completing the survey, which took on average
+10.43 minutes (\emph{SD} = 3.34).
+
 \subsection{Material}\label{material}
 
+\textbf{Personality.} To assess personality traits (openness to
+experiences, conscientiousness, extraversion, agreeableness, and
+emotional stability), respondents completed the Ten Item Personality
+Inventory (Gosling, Rentfrow, \& Swann Jr, 2003). Participants were
+asked to indicate the extent to which they agreed or disagreed with
+statements describing themselves (e.g. \enquote{Extraverted,
+enthusiastic}; \enquote{Critical, quarrelsome}). Respondents rated each
+statement on a 7-point likert scale (1 = Strongly Disagree to 7 =
+Strongly Agree). Responses were coded such that higher values reflected
+greater identification with the personality trait.
+
+\textbf{Social and Economic Conservatism.} To assess participant levels
+of conservatism, respondents completed the 12-item Social and Economic
+Conservatism Scale (Everett, 2013). Participants were asked to indicate
+the extent to which they feel positively or negatively about seven
+social issues and five economic issues (eg. Abortion; Fiscal
+Responsibility). Respondents rated each issue on a 100-point scale (0
+indicates greater negativity and 100 indicates greater positivity).
+Responses were coded such that higher values reflected greater levels of
+conservatism.
+
+\textbf{Additional Measures.} Incidental affect was induced via video
+clips (Schaefer, Nils, Sanchez, \& Philippot, 2010). Clips from
+\emph{The Shining} and \emph{The Blair Witch Project} were used to
+induce fear, clips from \emph{Seven} and \emph{Schindler's List} were
+used to induce anger, and clips from \emph{Blue} were used to induce no
+emotion. Participants also read a speech on the prevalence of
+homelessness in the United States and a corresponding policy varying in
+complexity and affiliation.
+
+Participants completed additional measures, including an adjusted PANAS
+Affect Scale assessing current emotional state (Watson, Clark, \&
+Tellegen, 1988), the 18-Point Need for Cognition Scale assessing need
+for cognition (Cacioppo, Petty, \& Feng Kao, 1984), the 10-Point Emotion
+Regulation Questionnaire assessing the use of two emotional regulation
+strategies, cognitive reappraisal and expressive supression (Gross \&
+John, 2003), and demographic information, including gender, ethnicity,
+age, and political orientation and affiliation.
+
 \subsection{Procedure}\label{procedure}
+
+Participants accessed the survey through the Amazon Mechanical Turk
+website. Once informed consent was confirmed, participants were randomly
+assigned to watch a video intended to induce primarily fear, anger, or
+no emotion. After watching the video, each participant was presented
+with information describing the prevalance of homelessness in the United
+States. Participants were then randomly assigned to read a policy
+statement addressing homelessness that was either simple or complex, and
+liberal or conservative, and were then asked to answer questions
+measuring their beliefs about the policy. Additional measures followed
+measuring social and economic conservatism, personality traits, current
+affective state, neeed for cognition, and emotional regulation.
+Participants concluded the study by providing demographic information.
 
@@
 
-In order to understand the relation between conservatism and
-personality, we first looked at Big Five personality trait (Openness to
-Experience, Conscientiousness, Extraversion, Agreeableness, and
-Emotional Stability) scores across the spectrum of Social Conservatism
-(Table 1) and Economic Conservatism (Table 2) scores.
+In order to explore relation between conservatism and personality, we
+created a table of the Big Five personality trait (openness to
+experiences, conscientiousness, extraversion, agreeableness, and
+emotional stability) scores across different levels of social (see Table
+1) and economic (see Table 2) conservatism.
 
-To see whether there were significant relations between Social
-Conservatism and the Big Five, we then ran a multiple regression
-predicting Social Conservatism from the Big Five personality traits. A
-significant regression equation was found (\emph{F}(5, 125) = 5.051,
-\emph{p} \textless{} .001), with an adjusted \(R^2\) of 0.135 (Table 2).
-Thus, personality traits taken together explained 13.48\% of variance in
-Social Conservatism scores. Participants' predicted Social Conservatism
-scores were equal to 25.82 - 3.73(Openness to Experience) +
-0.07(Conscientiousness) + 1.56(Extraversion) + 3.93(Agreeableness) +
-4.30(Emotional Stability). Agreeableness and Emotional Stability were
-significant predictors of Social Conservatism.
+To see whether there were significant relations between social
+conservatism and the Big Five traits, we then ran a multiple regression
+predicting social conservatism from the Big Five personality traits. We
+found that together the personality traits explain about 13.5\% of the
+variance in social conservatism scores, \emph{F}(5, 125) = 5.05,
+\emph{p} \textless{} .001, with an adjusted \(R^2\) of .14 (see Table
+3). We found that agreeablessness, \(\beta\) = 3.93, \emph{t}(125) =
+2.40, \emph{p} = .018, and emotional stability, \(\beta\) = 4.30,
+\emph{t}(125) = 2.37, \emph{p} = .020, significantly predict social
+conservatism, such that, controlling for the other personality traits,
+those who scored higher on agreeableness and emotional stability
+measures tended to also score higher on the social conservatism measure.
+Additionally, openness to experiences margionally predicted social
+conservatism, \(\beta\) = -3.73, \emph{t}(125) = -1.96, \emph{p} = .052,
+such that, controlling for other personality traits, those who scored
+higher on conservatism tended to score lower on the openness to
+experience measure.
 
-To see whether there were significant relations between Economic
-Conservatism and the Big Five, we then ran a multiple regression
-predicting Economic Conservatism from the Big Five personality traits.
-No significant regression equation was found (\emph{F}(5, 125) = 2.207,
-\emph{p} = .058) (Table 3). Thus, personality traits taken together did
-not significantly explain variance in Economic Conservatism scores.
-However, Openness to Experience was a significant predictor of Economic
-Conservatism.
+To see whether there were significant relations between economic
+conservatism and the Big Five traits, we then ran a multiple regression
+predicting economic conservatism from the Big Five personality traits.
+The personality traits taken together did not significantly explain
+variance in economic conservatism scores, \emph{F}(5, 125) = 2.21,
+\emph{p} = .058 (see Table 4). However, openness to experience was a
+significant predictor of economic conservatism, \(\beta\) = -3.79,
+\emph{t}(125) = -2.35, \emph{p} = .021, such that, controlling for other
+personality traits, those who scored high on economic conservatism
+subscale tended to score lower on the openness to experiences measure.
 
@@
 conservatism, we examined the correlation between social and economic
-conservatism scores, and found it to be r = 0.65. Neither social nor
-economic extraversion were strongly correlated with any of the Big Five
-personality traits.
+conservatism scores, and found it to be \emph{r} = .65. Neither social
+nor economic extraversion were strongly correlated with any of the Big
+Five personality traits (see Figure 1).
 
@@
 
+\hypertarget{ref-cacioppo1984efficient}{}
+Cacioppo, J. T., Petty, R. E., \& Feng Kao, C. (1984). The efficient
+assessment of need for cognition. \emph{Journal of Personality
+Assessment}, \emph{48}(3), 306--307.
+
 \hypertarget{ref-R-rio}{}
@@
 \emph{Rio: A swiss-army knife for data file i/o}.
+
+\hypertarget{ref-everett201312}{}
+Everett, J. A. (2013). The 12 item social and economic conservatism
+scale (secs). \emph{PloS One}, \emph{8}(12), e82131.
 
@@
 \url{https://CRAN.R-project.org/package=viridisLite}
+
+\hypertarget{ref-gosling2003very}{}
+Gosling, S. D., Rentfrow, P. J., \& Swann Jr, W. B. (2003). A very brief
+measure of the big-five personality domains. \emph{Journal of Research
+in Personality}, \emph{37}(6), 504--528.
+
+\hypertarget{ref-gross2003individual}{}
+Gross, J. J., \& John, O. P. (2003). Individual differences in two
+emotion regulation processes: Implications for affect, relationships,
+and well-being. \emph{Journal of Personality and Social Psychology},
+\emph{85}(2), 348.
 
@@
 \url{https://CRAN.R-project.org/package=psych}
+
+\hypertarget{ref-schaefer2010}{}
+Schaefer, A., Nils, F., Sanchez, X., \& Philippot, P. (2010). Assessing
+the effectiveness of a large database of emotion-eliciting films: A new
+tool for emotion researchers. \emph{Cognition and Emotion},
+\emph{24}(7), 1153--1172.
+
+\hypertarget{ref-watson1988development}{}
+Watson, D., Clark, L. A., \& Tellegen, A. (1988). Development and
+validation of brief measures of positive and negative affect: The panas
+scales. \emph{Journal of Personality and Social Psychology},
+\emph{54}(6), 1063.
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/correlations-1.pdf}
-\caption{}
+\includegraphics{manuscript_files/figure-latex/figure1-1.pdf}
+\caption{\label{fig:figure1}A correlation heatmap demonstrating the
+correlations between the Big Five personality traits and social and
+economic conservatism.}
 \end{figure}
 
-\includegraphics{manuscript_files/figure-latex/figure1-1.pdf}
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
+\caption{\label{fig:figure2}We found a significant positive relation between
+emotional stability and social conservatism, a positive relation between
+agreeableness and social conservatism, and a negative relation between
+openness to experiences and economic conservatism.}
+\end{figure}
 

### 2019-12-11 scripts/manuscript.tex
Commits Related to Merge

@@
 
-\authornote{This project was completed as part of the EDLD
-Introduction to Data Science class at the University of Oregon.
+\authornote{This project was completed as part of the EDLD Introduction to Data Science class at the University of Oregon.
 
-Correspondence concerning this article should be addressed to Sarah
-Dimakis, University of Oregon, Eugene, OR. E-mail:
-\href{mailto:sdimakis@uoregon.edu}{\nolinkurl{sdimakis@uoregon.edu}}}
+Correspondence concerning this article should be addressed to Sarah Dimakis, University of Oregon, Eugene, OR. E-mail: \href{mailto:sdimakis@uoregon.edu}{\nolinkurl{sdimakis@uoregon.edu}}}
 
@@
 
-\section{Methods}\label{methods}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
-\subsection{Participants}\label{participants}
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
-Two-hundred U.S. adults were recruited via Amazon Mechanical Turk to
-participate in a study listed as \enquote{Psychology and society
-survey.} Participants were removed for completing the survey quicker
-than predetermined time cutoffs or failing to pass attention checks. Of
-the remaining 131 participants, who were 20 to 68 years old (\emph{M} =
-40.55, \emph{SD} = 11.98), 54.2\% identified as female and 45.8\%
-identified as male, while 77.1\% identified as White of Caucasian, 7.6\%
-as African American or Black, 6.1\% as Hispanic or Latinx, 5.3\% as
-Asian or Asian American, 0.8\% as Native American, and 9.2\% as
-\enquote{Other.} The sample leaned liberal, with 45\% affiliated with
-the Democratic Party, 23.7\% affiliated with the Republican Party,
-22.1\% affiliated with no party, and 9.2\% affiliated with the Green
-Party, Libertarian Party, or another party. The participants were
-compensated \$1.50 for completing the survey, which took on average
-10.43 minutes (\emph{SD} = 3.34).
+Two-hundred U.S.
+adults were recruited via Amazon Mechanical Turk to participate in a study listed as \enquote{Psychology and society survey.} Participants were removed for completing the survey quicker than predetermined time cutoffs or failing to pass attention checks.
+Of the remaining 131 participants, who were 20 to 68 years old (\emph{M} = 40.55, \emph{SD} = 11.98), 54.2\% identified as female and 45.8\% identified as male, while 77.1\% identified as White of Caucasian, 7.6\% as African American or Black, 6.1\% as Hispanic or Latinx, 5.3\% as Asian or Asian American, 0.8\% as Native American, and 9.2\% as \enquote{Other.} The sample leaned liberal, with 45\% affiliated with the Democratic Party, 23.7\% affiliated with the Republican Party, 22.1\% affiliated with no party, and 9.2\% affiliated with the Green Party, Libertarian Party, or another party.
+The participants were compensated \$1.50 for completing the survey, which took on average 10.43 minutes (\emph{SD} = 3.34).
 
-\subsection{Material}\label{material}
+\hypertarget{material}{%
+\subsection{Material}\label{material}}
 
-\textbf{Personality.} To assess personality traits (openness to
-experiences, conscientiousness, extraversion, agreeableness, and
-emotional stability), respondents completed the Ten Item Personality
-Inventory (Gosling, Rentfrow, \& Swann Jr, 2003). Participants were
-asked to indicate the extent to which they agreed or disagreed with
-statements describing themselves (e.g. \enquote{Extraverted,
-enthusiastic}; \enquote{Critical, quarrelsome}). Respondents rated each
-statement on a 7-point likert scale (1 = Strongly Disagree to 7 =
-Strongly Agree). Responses were coded such that higher values reflected
-greater identification with the personality trait.
+\textbf{Personality.} To assess personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability), respondents completed the Ten Item Personality Inventory (Gosling, Rentfrow, \& Swann Jr, 2003).
+Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g.
+\enquote{Extraverted, enthusiastic}; \enquote{Critical, quarrelsome}).
+Respondents rated each statement on a 7-point likert scale (1 = Strongly Disagree to 7 = Strongly Agree).
+Responses were coded such that higher values reflected greater identification with the personality trait.
 
-\textbf{Social and Economic Conservatism.} To assess participant levels
-of conservatism, respondents completed the 12-item Social and Economic
-Conservatism Scale (Everett, 2013). Participants were asked to indicate
-the extent to which they feel positively or negatively about seven
-social issues and five economic issues (eg. Abortion; Fiscal
-Responsibility). Respondents rated each issue on a 100-point scale (0
-indicates greater negativity and 100 indicates greater positivity).
-Responses were coded such that higher values reflected greater levels of
-conservatism.
+\textbf{Social and Economic Conservatism.} To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale (Everett, 2013).
+Participants were asked to indicate the extent to which they feel positively or negatively about seven social issues and five economic issues (eg.
+Abortion; Fiscal Responsibility).
+Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity).
+Responses were coded such that higher values reflected greater levels of conservatism.
 
-\textbf{Additional Measures.} Incidental affect was induced via video
-clips (Schaefer, Nils, Sanchez, \& Philippot, 2010). Clips from
-\emph{The Shining} and \emph{The Blair Witch Project} were used to
-induce fear, clips from \emph{Seven} and \emph{Schindler's List} were
-used to induce anger, and clips from \emph{Blue} were used to induce no
-emotion. Participants also read a speech on the prevalence of
-homelessness in the United States and a corresponding policy varying in
-complexity and affiliation.
+\textbf{Additional Measures.} Incidental affect was induced via video clips (Schaefer, Nils, Sanchez, \& Philippot, 2010).
+Clips from \emph{The Shining} and \emph{The Blair Witch Project} were used to induce fear, clips from \emph{Seven} and \emph{Schindler's List} were used to induce anger, and clips from \emph{Blue} were used to induce no emotion.
+Participants also read a speech on the prevalence of homelessness in the United States and a corresponding policy varying in complexity and affiliation.
 
-Participants completed additional measures, including an adjusted PANAS
-Affect Scale assessing current emotional state (Watson, Clark, \&
-Tellegen, 1988), the 18-Point Need for Cognition Scale assessing need
-for cognition (Cacioppo, Petty, \& Feng Kao, 1984), the 10-Point Emotion
-Regulation Questionnaire assessing the use of two emotional regulation
-strategies, cognitive reappraisal and expressive supression (Gross \&
-John, 2003), and demographic information, including gender, ethnicity,
-age, and political orientation and affiliation.
+Participants completed additional measures, including an adjusted PANAS Affect Scale assessing current emotional state (Watson, Clark, \& Tellegen, 1988), the 18-Point Need for Cognition Scale assessing need for cognition (Cacioppo, Petty, \& Feng Kao, 1984), the 10-Point Emotion Regulation Questionnaire assessing the use of two emotional regulation strategies, cognitive reappraisal and expressive supression (Gross \& John, 2003), and demographic information, including gender, ethnicity, age, and political orientation and affiliation.
 
-\subsection{Procedure}\label{procedure}
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
-Participants accessed the survey through the Amazon Mechanical Turk
-website. Once informed consent was confirmed, participants were randomly
-assigned to watch a video intended to induce primarily fear, anger, or
-no emotion. After watching the video, each participant was presented
-with information describing the prevalance of homelessness in the United
-States. Participants were then randomly assigned to read a policy
-statement addressing homelessness that was either simple or complex, and
-liberal or conservative, and were then asked to answer questions
-measuring their beliefs about the policy. Additional measures followed
-measuring social and economic conservatism, personality traits, current
-affective state, neeed for cognition, and emotional regulation.
+Participants accessed the survey through the Amazon Mechanical Turk website.
+Once informed consent was confirmed, participants were randomly assigned to watch a video intended to induce primarily fear, anger, or no emotion.
+After watching the video, each participant was presented with information describing the prevalance of homelessness in the United States.
+Participants were then randomly assigned to read a policy statement addressing homelessness that was either simple or complex, and liberal or conservative, and were then asked to answer questions measuring their beliefs about the policy.
+Additional measures followed measuring social and economic conservatism, personality traits, current affective state, neeed for cognition, and emotional regulation.
 Participants concluded the study by providing demographic information.
 
-\subsection{Data analysis}\label{data-analysis}
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
 
-We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
-\emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham,
-François, Henry, \& Müller, 2019), \emph{forcats} (Version 0.4.0;
-Wickham, 2019a), \emph{ggplot2} (Version 3.2.1; Wickham, 2016),
-\emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0;
-Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja}
-(Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12;
-Revelle, 2018), \emph{purrr} (Version 0.3.3; Henry \& Wickham, 2019),
-\emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018),
-\emph{rio} (Version 0.5.16; C.-h. Chan, Chan, Leeper, \& Becker, 2018),
-\emph{stringr} (Version 1.4.0; Wickham, 2019b), \emph{tibble} (Version
-2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \&
-Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017),
-\emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and
-\emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
+We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
 
-\section{Results}\label{results}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-In order to explore relation between conservatism and personality, we
-created a table of the Big Five personality trait (openness to
-experiences, conscientiousness, extraversion, agreeableness, and
-emotional stability) scores across different levels of social (see Table
-1) and economic (see Table 2) conservatism.
+In order to explore relation between conservatism and personality, we created a table of the Big Five personality trait (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability) scores across different levels of social (see Table 1) and economic (see Table 2) conservatism.
 
-To see whether there were significant relations between social
-conservatism and the Big Five traits, we then ran a multiple regression
-predicting social conservatism from the Big Five personality traits. We
-found that together the personality traits explain about 13.5\% of the
-variance in social conservatism scores, \emph{F}(5, 125) = 5.05,
-\emph{p} \textless{} .001, with an adjusted \(R^2\) of .14 (see Table
-3). We found that agreeablessness, \(\beta\) = 3.93, \emph{t}(125) =
-2.40, \emph{p} = .018, and emotional stability, \(\beta\) = 4.30,
-\emph{t}(125) = 2.37, \emph{p} = .020, significantly predict social
-conservatism, such that, controlling for the other personality traits,
-those who scored higher on agreeableness and emotional stability
-measures tended to also score higher on the social conservatism measure.
-Additionally, openness to experiences margionally predicted social
-conservatism, \(\beta\) = -3.73, \emph{t}(125) = -1.96, \emph{p} = .052,
-such that, controlling for other personality traits, those who scored
-higher on conservatism tended to score lower on the openness to
-experience measure.
+To see whether there were significant relations between social conservatism and the Big Five traits, we then ran a multiple regression predicting social conservatism from the Big Five personality traits.
+We found that together the personality traits explain about 13.5\% of the variance in social conservatism scores, \emph{F}(5, 125) = 5.05, \emph{p} \textless{} .001, with an adjusted \(R^2\) of .14 (see Table 3).
+We found that agreeablessness, \(\beta\) = 3.93, \emph{t}(125) = 2.40, \emph{p} = .018, and emotional stability, \(\beta\) = 4.30, \emph{t}(125) = 2.37, \emph{p} = .020, significantly predict social conservatism, such that, controlling for the other personality traits, those who scored higher on agreeableness and emotional stability measures tended to also score higher on the social conservatism measure.
+Additionally, openness to experiences margionally predicted social conservatism, \(\beta\) = -3.73, \emph{t}(125) = -1.96, \emph{p} = .052, such that, controlling for other personality traits, those who scored higher on conservatism tended to score lower on the openness to experience measure.
 
-To see whether there were significant relations between economic
-conservatism and the Big Five traits, we then ran a multiple regression
-predicting economic conservatism from the Big Five personality traits.
-The personality traits taken together did not significantly explain
-variance in economic conservatism scores, \emph{F}(5, 125) = 2.21,
-\emph{p} = .058 (see Table 4). However, openness to experience was a
-significant predictor of economic conservatism, \(\beta\) = -3.79,
-\emph{t}(125) = -2.35, \emph{p} = .021, such that, controlling for other
-personality traits, those who scored high on economic conservatism
-subscale tended to score lower on the openness to experiences measure.
+To see whether there were significant relations between economic conservatism and the Big Five traits, we then ran a multiple regression predicting economic conservatism from the Big Five personality traits.
+The personality traits taken together did not significantly explain variance in economic conservatism scores, \emph{F}(5, 125) = 2.21, \emph{p} = .058 (see Table 4).
+However, openness to experience was a significant predictor of economic conservatism, \(\beta\) = -3.79, \emph{t}(125) = -2.35, \emph{p} = .021, such that, controlling for other personality traits, those who scored high on economic conservatism subscale tended to score lower on the openness to experiences measure.
 
-To better understand the relation between social and economic
-conservatism, we examined the correlation between social and economic
-conservatism scores, and found it to be \emph{r} = .65. Neither social
-nor economic extraversion were strongly correlated with any of the Big
-Five personality traits (see Figure 1).
+To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be \emph{r} = .65.
+Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits (see Figure 1).
 
-\section{Discussion}\label{discussion}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 
-\section{References}\label{references}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 \begingroup
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-R-papaja}{}
-Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with
-R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\hypertarget{ref-cacioppo1984efficient}{}
-Cacioppo, J. T., Petty, R. E., \& Feng Kao, C. (1984). The efficient
-assessment of need for cognition. \emph{Journal of Personality
-Assessment}, \emph{48}(3), 306--307.
+\leavevmode\hypertarget{ref-cacioppo1984efficient}{}%
+Cacioppo, J. T., Petty, R. E., \& Feng Kao, C. (1984). The efficient assessment of need for cognition. \emph{Journal of Personality Assessment}, \emph{48}(3), 306--307.
 
-\hypertarget{ref-R-rio}{}
-Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018).
-\emph{Rio: A swiss-army knife for data file i/o}.
+\leavevmode\hypertarget{ref-R-rio}{}%
+Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.
 
-\hypertarget{ref-everett201312}{}
-Everett, J. A. (2013). The 12 item social and economic conservatism
-scale (secs). \emph{PloS One}, \emph{8}(12), e82131.
+\leavevmode\hypertarget{ref-everett201312}{}%
+Everett, J. A. (2013). The 12 item social and economic conservatism scale (secs). \emph{PloS One}, \emph{8}(12), e82131.
 
-\hypertarget{ref-R-janitor}{}
-Firke, S. (2019). \emph{Janitor: Simple tools for examining and cleaning
-dirty data}. Retrieved from
-\url{https://CRAN.R-project.org/package=janitor}
+\leavevmode\hypertarget{ref-R-janitor}{}%
+Firke, S. (2019). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
 
-\hypertarget{ref-R-viridis}{}
-Garnier, S. (2018a). \emph{Viridis: Default color maps from
-'matplotlib'}. Retrieved from
-\url{https://CRAN.R-project.org/package=viridis}
+\leavevmode\hypertarget{ref-R-viridis}{}%
+Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}
 
-\hypertarget{ref-R-viridisLite}{}
-Garnier, S. (2018b). \emph{ViridisLite: Default color maps from
-'matplotlib' (lite version)}. Retrieved from
-\url{https://CRAN.R-project.org/package=viridisLite}
+\leavevmode\hypertarget{ref-R-viridisLite}{}%
+Garnier, S. (2018b). \emph{ViridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}
 
-\hypertarget{ref-gosling2003very}{}
-Gosling, S. D., Rentfrow, P. J., \& Swann Jr, W. B. (2003). A very brief
-measure of the big-five personality domains. \emph{Journal of Research
-in Personality}, \emph{37}(6), 504--528.
+\leavevmode\hypertarget{ref-gosling2003very}{}%
+Gosling, S. D., Rentfrow, P. J., \& Swann Jr, W. B. (2003). A very brief measure of the big-five personality domains. \emph{Journal of Research in Personality}, \emph{37}(6), 504--528.
 
-\hypertarget{ref-gross2003individual}{}
-Gross, J. J., \& John, O. P. (2003). Individual differences in two
-emotion regulation processes: Implications for affect, relationships,
-and well-being. \emph{Journal of Personality and Social Psychology},
-\emph{85}(2), 348.
+\leavevmode\hypertarget{ref-gross2003individual}{}%
+Gross, J.
+J., \& John, O.
+P.
+(2003).
+Individual differences in two emotion regulation processes: Implications for affect, relationships, and well-being.
+\emph{Journal of Personality and Social Psychology}, \emph{85}(2), 348.
 
-\hypertarget{ref-R-purrr}{}
-Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
-tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
 
-\hypertarget{ref-R-here}{}
-Müller, K. (2017). \emph{Here: A simpler way to find your files}.
-Retrieved from \url{https://CRAN.R-project.org/package=here}
+\leavevmode\hypertarget{ref-R-here}{}%
+Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}
 
-\hypertarget{ref-R-tibble}{}
-Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
-Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
-\hypertarget{ref-R-base}{}
-R Core Team. (2019). \emph{R: A language and environment for statistical
-computing}. Vienna, Austria: R Foundation for Statistical Computing.
-Retrieved from \url{https://www.R-project.org/}
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
-\hypertarget{ref-R-psych}{}
-Revelle, W. (2018). \emph{Psych: Procedures for psychological,
-psychometric, and personality research}. Evanston, Illinois:
-Northwestern University. Retrieved from
-\url{https://CRAN.R-project.org/package=psych}
+\leavevmode\hypertarget{ref-R-psych}{}%
+Revelle, W.
+(2018).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
 
-\hypertarget{ref-schaefer2010}{}
-Schaefer, A., Nils, F., Sanchez, X., \& Philippot, P. (2010). Assessing
-the effectiveness of a large database of emotion-eliciting films: A new
-tool for emotion researchers. \emph{Cognition and Emotion},
-\emph{24}(7), 1153--1172.
+\leavevmode\hypertarget{ref-schaefer2010}{}%
+Schaefer, A., Nils, F., Sanchez, X., \& Philippot, P.
+(2010).
+Assessing the effectiveness of a large database of emotion-eliciting films: A new tool for emotion researchers.
+\emph{Cognition and Emotion}, \emph{24}(7), 1153--1172.
 
-\hypertarget{ref-watson1988development}{}
-Watson, D., Clark, L. A., \& Tellegen, A. (1988). Development and
-validation of brief measures of positive and negative affect: The panas
-scales. \emph{Journal of Personality and Social Psychology},
-\emph{54}(6), 1063.
+\leavevmode\hypertarget{ref-watson1988development}{}%
+Watson, D., Clark, L.
+A., \& Tellegen, A.
+(1988).
+Development and validation of brief measures of positive and negative affect: The panas scales.
+\emph{Journal of Personality and Social Psychology}, \emph{54}(6), 1063.
 
-\hypertarget{ref-R-ggplot2}{}
-Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
-Springer-Verlag New York. Retrieved from
-\url{https://ggplot2.tidyverse.org}
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
 
-\hypertarget{ref-R-tidyverse}{}
-Wickham, H. (2017). \emph{Tidyverse: Easily install and load the
-'tidyverse'}. Retrieved from
-\url{https://CRAN.R-project.org/package=tidyverse}
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}
 
-\hypertarget{ref-R-forcats}{}
-Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical
-variables (factors)}. Retrieved from
-\url{https://CRAN.R-project.org/package=forcats}
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
 
-\hypertarget{ref-R-stringr}{}
-Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for
-common string operations}. Retrieved from
-\url{https://CRAN.R-project.org/package=stringr}
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
 
-\hypertarget{ref-R-tidyr}{}
-Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}.
-Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
 
-\hypertarget{ref-R-dplyr}{}
-Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr:
-A grammar of data manipulation}. Retrieved from
-\url{https://CRAN.R-project.org/package=dplyr}
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
 
-\hypertarget{ref-R-readr}{}
-Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read
-rectangular text data}. Retrieved from
-\url{https://CRAN.R-project.org/package=readr}
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
 
-\hypertarget{ref-R-knitr}{}
-Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.).
-Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from
-\url{https://yihui.name/knitr/}
+Call:corr.test(x = untidy\(economic_conservatism, y = untidy\)social\_conservatism)
+Correlation matrix
+{[}1{]} 0.65
+Sample Size
+{[}1{]} 131
+Probability values adjusted for multiple tests.
+{[}1{]} 0
 
-Call:corr.test(x =
-untidy\(economic_conservatism, y = untidy\)social\_conservatism)
-Correlation matrix {[}1{]} 0.65 Sample Size {[}1{]} 131 Probability
-values adjusted for multiple tests. {[}1{]} 0
-
-To see confidence intervals of the correlations, print with the
-short=FALSE option
+To see confidence intervals of the correlations, print with the short=FALSE option
 
@@
 \includegraphics{manuscript_files/figure-latex/figure1-1.pdf}
-\caption{\label{fig:figure1}A correlation heatmap demonstrating the
-correlations between the Big Five personality traits and social and
-economic conservatism.}
+\caption{\label{fig:figure1}A correlation heatmap demonstrating the correlations between the Big Five personality traits and social and economic conservatism.}
 \end{figure}
@@
 \includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
-\caption{\label{fig:figure2}We found a significant positive relation between
-emotional stability and social conservatism, a positive relation between
-agreeableness and social conservatism, and a negative relation between
-openness to experiences and economic conservatism.}
+\caption{\label{fig:figure2}We found a significant positive relation between emotional stability and social conservatism, a positive relation between agreeableness and social conservatism, and a negative relation between openness to experiences and economic conservatism.}
 \end{figure}

### 2019-12-11 scripts/manuscript.Rmd
added intro

@@
 
-```{r table1, echo = FALSE, results = "asis"}
-#this table is of the mean personality trait scores by social conservatism scores
-tidy_table_sc <- tidy %>% 
-  filter(conservatism_type == 'Social conservatism') %>%
-  mutate(conservatism_score = case_when(       
-      conservatism_score <= 19 & conservatism_score >= 0 ~ "[0-19]",
-      conservatism_score <= 39 & conservatism_score >= 20 ~ "[20-39]",
-      conservatism_score <= 59 & conservatism_score >= 40 ~ "[40-59]",
-      conservatism_score <= 79 & conservatism_score >= 60 ~ "[60-79]",
-      TRUE ~ "[80-100]"))
-tidy_table_sc <- tidy_table_sc %>%
-  group_by(personality_trait, conservatism_score) %>% 
-  summarize(mean_personality_score = mean(personality_score)) %>% 
-  pivot_wider(names_from = conservatism_score, values_from = mean_personality_score)
+The Five Factor Model is a widely used framework for measuring and classifying personality into five dimensions [@goldberg1992development; @mccrae1999age; @john1999big].
+Those who score high in *openness to experiences* tend to describe themselves as curious, deep thinkers compared to those who score low in openness to experience, who describe themselves as traditional and conventional.
+Those who score high in *conscientiousness* are generally reliable and hardworking, while those who score low in conscientiousness tend to be disorganized and impulsive.
+Those high in *extraversion* are talkative and energetic, while those high in introversion are reserved and quiet.
+Those who score high in *agreeableness* describe themselves as kind and trusting, while those who score low in agreeableness say they are quarrelsome and critical.
+And lastly, those who are high in *emotional stability* are calm individuals who handle stress well, while those high in neuroticism tend to be anxious individuals who are easily upset.
 
-apa_table(tidy_table_sc, 
-            caption = "Mean Personality Trait Scores by Social Conservatism Score",
-          col_spanners = list(`Social Conservatism Score` = c(2, 6)),
-          note = "Personality trait scores reported on a 1-7 scale.")
-```
+Given that these personality traits have been found to predict a multitude of cognitions and behaviors, from well-being to cognitive abilities [@hayes2003big; @curtis2015relationship; @barlett2012direct], previous studies have looked at whether personality can predict political beliefs and affiliation [@jost2009personality; @hirsh2010compassionate].
+The most robust findings are that openness to experience is positively correlated with liberalness [@carney2008secret; @ekehammar2004matters], while conscientiousness is positively correlated with conservativeness [@stenner2005rights; @barbaranelli2007voters].
 
-```{r table2, echo = FALSE, results = "asis"}
-tidy_table_ec <- tidy %>% 
-  filter(conservatism_type == 'Economic conservatism') %>% 
-  mutate(conservatism_score = case_when(       
-      conservatism_score <= 19 & conservatism_score >= 0 ~ "[0-19]",
-      conservatism_score <= 39 & conservatism_score >= 20 ~ "[20-39]",
-      conservatism_score <= 59 & conservatism_score >= 40 ~ "[40-59]",
-      conservatism_score <= 79 & conservatism_score >= 60 ~ "[60-79]",
-      TRUE ~ "[80-100]"))
-tidy_table_ec <- tidy_table_ec %>% 
-  group_by(personality_trait, conservatism_score) %>% 
-  summarize(mean_personality_score = mean(personality_score)) %>% 
-  pivot_wider(names_from = conservatism_score, values_from = mean_personality_score)
+This project uses data from a larger study that measured political beliefs and the big five personality traits.
+Consistent with prior research, we hypothesize that we will find a positive relation between conscientiousness and conservatism and a negative relation between openness to experience and conservatism.
+We will first make exploratory tables and plots that explore the relation between all big five personality traits and social and economic conservatism, and then we will run two linear models with traits as predictors and types of conservatism as outcome variables.
 
-apa_table(tidy_table_ec, 
-            caption = "Mean Personality Trait Scores by Economic Conservatism Score",
-          col_spanners = list(`Economic Conservatism Score` = c(2, 6)),
-          note = "Personality trait scores reported on a 1-7 scale.")
-```
-
-```{r linearmodels_conservatism_ocean, include = FALSE}
-untidy <- tidy %>% 
-  pivot_wider(names_from = conservatism_type, values_from = conservatism_score) %>% 
-  pivot_wider(names_from = personality_trait, values_from = personality_score) %>% 
-  rename(social_conservatism = 'Social conservatism',
-         economic_conservatism = 'Economic conservatism',
-         openness_to_experiences = 'Openness to experiences',
-         emotional_stability = 'Emotional stability')
-
-sc_ocean <- lm(social_conservatism ~ openness_to_experiences + Conscientiousness + Extraversion + Agreeableness + emotional_stability,
-              data = untidy)
-summary(sc_ocean)
-plot(scale(residuals(sc_ocean)) ~ scale(fitted(sc_ocean)), xlab="Social Conservatism Scores", ylab = "Scaled Residuals")
-
-ec_ocean <- lm(economic_conservatism ~ openness_to_experiences + Conscientiousness + Extraversion + Agreeableness + emotional_stability,
-              data = untidy)
-summary(ec_ocean)
-plot(scale(residuals(ec_ocean)) ~ scale(fitted(ec_ocean)), xlab="Economic Conservatism Scores", ylab = "Scaled Residuals")
-```
-
-```{r linearmodels_conservatism_ocean_tables, echo = FALSE, results = "asis"}
-apa_sc_ocean <- apa_print(sc_ocean)
-apa_sc_ocean$table %>% 
-  apa_table(caption = "Regression Table Predicting Social Conservatism From Big-Five Personality Traits.", note = "Residual standard error: 25.13 on 125 degrees of freedom.
-Multiple R-squared: 0.168, Adjusted R-squared: 0.135. F(5, 125): 5.051, p-value: 0.0003.", escape = FALSE)
-
-apa_ec_ocean <- apa_print(ec_ocean)
-apa_ec_ocean$table %>% 
-  apa_table(caption = "Regression Table Predicting Economic Conservatism From Big-Five Personality Traits.", note = "Residual standard error: 21.3 on 125 degrees of freedom.
-Multiple R-squared: 0.081, Adjusted R-squared: 0.044.
-F(5, 125): 2.207, p-value: 0.058.", escape = FALSE)
-```
-
-# Methods
+# Method
 
 ```{r, include = FALSE}
+#I'm am going to use these descriptives in the participants section
 #Age statistics
@@
 
+```{r linearmodels_conservatism_ocean, include = FALSE}
+untidy <- tidy %>% 
+  pivot_wider(names_from = conservatism_type, values_from = conservatism_score) %>% 
+  pivot_wider(names_from = personality_trait, values_from = personality_score) %>% 
+  rename(social_conservatism = 'Social conservatism',
+         economic_conservatism = 'Economic conservatism',
+         openness_to_experiences = 'Openness to experiences',
+         emotional_stability = 'Emotional stability')
+
+sc_ocean <- lm(social_conservatism ~ openness_to_experiences + Conscientiousness + Extraversion + Agreeableness + emotional_stability,
+              data = untidy)
+summary(sc_ocean)
+plot(scale(residuals(sc_ocean)) ~ scale(fitted(sc_ocean)), xlab="Social Conservatism Scores", ylab = "Scaled Residuals")
+
+ec_ocean <- lm(economic_conservatism ~ openness_to_experiences + Conscientiousness + Extraversion + Agreeableness + emotional_stability,
+              data = untidy)
+summary(ec_ocean)
+plot(scale(residuals(ec_ocean)) ~ scale(fitted(ec_ocean)), xlab="Economic Conservatism Scores", ylab = "Scaled Residuals")
+```
+
 # Results
@@
 <div id = "refs"></div>
+```{r table1, echo = FALSE, results = "asis"}
+#this table is of the mean personality trait scores by social conservatism scores
+tidy_table_sc <- tidy %>% 
+  filter(conservatism_type == 'Social conservatism') %>%
+  mutate(conservatism_score = case_when(       
+      conservatism_score <= 19 & conservatism_score >= 0 ~ "[0-19]",
+      conservatism_score <= 39 & conservatism_score >= 20 ~ "[20-39]",
+      conservatism_score <= 59 & conservatism_score >= 40 ~ "[40-59]",
+      conservatism_score <= 79 & conservatism_score >= 60 ~ "[60-79]",
+      TRUE ~ "[80-100]"))
+tidy_table_sc <- tidy_table_sc %>%
+  group_by(personality_trait, conservatism_score) %>% 
+  summarize(mean_personality_score = mean(personality_score)) %>% 
+  pivot_wider(names_from = conservatism_score, values_from = mean_personality_score)
+
+apa_table(tidy_table_sc, 
+            caption = "Mean Personality Trait Scores by Social Conservatism Score",
+          col_spanners = list(`Social Conservatism Score` = c(2, 6)),
+          note = "Personality trait scores reported on a 1-7 scale.")
+```
+
+```{r table2, echo = FALSE, results = "asis"}
+tidy_table_ec <- tidy %>% 
+  filter(conservatism_type == 'Economic conservatism') %>% 
+  mutate(conservatism_score = case_when(       
+      conservatism_score <= 19 & conservatism_score >= 0 ~ "[0-19]",
+      conservatism_score <= 39 & conservatism_score >= 20 ~ "[20-39]",
+      conservatism_score <= 59 & conservatism_score >= 40 ~ "[40-59]",
+      conservatism_score <= 79 & conservatism_score >= 60 ~ "[60-79]",
+      TRUE ~ "[80-100]"))
+tidy_table_ec <- tidy_table_ec %>% 
+  group_by(personality_trait, conservatism_score) %>% 
+  summarize(mean_personality_score = mean(personality_score)) %>% 
+  pivot_wider(names_from = conservatism_score, values_from = mean_personality_score)
+
+apa_table(tidy_table_ec, 
+            caption = "Mean Personality Trait Scores by Economic Conservatism Score",
+          col_spanners = list(`Economic Conservatism Score` = c(2, 6)),
+          note = "Personality trait scores reported on a 1-7 scale.")
+```
+
+```{r table3, echo = FALSE, results = "asis"}
+apa_sc_ocean <- apa_print(sc_ocean)
+apa_sc_ocean$table %>% 
+  apa_table(caption = "Regression Table Predicting Social Conservatism From Big-Five Personality Traits.", note = "Residual standard error: 25.13 on 125 degrees of freedom.
+Multiple R-squared: 0.168, Adjusted R-squared: 0.135. F(5, 125): 5.051, p-value: 0.0003.", escape = FALSE)
+```
+
+```{r table4, echo = FALSE, results = "asis"}
+apa_ec_ocean <- apa_print(ec_ocean)
+apa_ec_ocean$table %>% 
+  apa_table(caption = "Regression Table Predicting Economic Conservatism From Big-Five Personality Traits.", note = "Residual standard error: 21.3 on 125 degrees of freedom.
+Multiple R-squared: 0.081, Adjusted R-squared: 0.044.
+F(5, 125): 2.207, p-value: 0.058.", escape = FALSE)
+```
 

### 2019-12-11 scripts/manuscript.tex
added intro

--- 2019-12-10 scripts/manuscript.tex
@@
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:table1}Mean Personality Trait Scores by Social Conservatism Score}
-\begin{tabular}{llllll}
-\toprule
- & \multicolumn{5}{c}{Social Conservatism Score} \\
-\cmidrule(r){2-6}
-personality\_trait & \multicolumn{1}{c}{[0-19]} & \multicolumn{1}{c}{[20-39]} & \multicolumn{1}{c}{[40-59]} & \multicolumn{1}{c}{[60-79]} & \multicolumn{1}{c}{[80-100]}\\
-\midrule
-Agreeableness & 4.67 & 5.20 & 4.88 & 5.76 & 5.90\\
-Conscientiousness & 5.37 & 5.44 & 5.32 & 5.84 & 6.03\\
-Emotional stability & 4.07 & 4.38 & 4.82 & 5.50 & 5.57\\
-Extraversion & 2.73 & 3.16 & 3.57 & 3.90 & 3.72\\
-Openness to experiences & 4.93 & 5.40 & 5.43 & 5.25 & 5.12\\
-\bottomrule
-\addlinespace
-\end{tabular}
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Personality trait scores reported on a 1-7 scale.}
-\end{tablenotes}
-\end{threeparttable}
-\end{center}
-\end{table}
+The Five Factor Model is a widely used framework for measuring and
+classifying personality into five dimensions (Goldberg, 1992; John \&
+Srivastava, 1999; McCrae et al., 1999). Those who score high in
+\emph{openness to experiences} tend to describe themselves as curious,
+deep thinkers compared to those who score low in openness to experience,
+who describe themselves as traditional and conventional. Those who score
+high in \emph{conscientiousness} are generally reliable and hardworking,
+while those who score low in conscientiousness tend to be disorganized
+and impulsive. Those high in \emph{extraversion} are talkative and
+energetic, while those high in introversion are reserved and quiet.
+Those who score high in \emph{agreeableness} describe themselves as kind
+and trusting, while those who score low in agreeableness say they are
+quarrelsome and critical. And lastly, those who are high in
+\emph{emotional stability} are calm individuals who handle stress well,
+while those high in neuroticism tend to be anxious individuals who are
+easily upset.
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:table2}Mean Personality Trait Scores by Economic Conservatism Score}
-\begin{tabular}{llllll}
-\toprule
- & \multicolumn{5}{c}{Economic Conservatism Score} \\
-\cmidrule(r){2-6}
-personality\_trait & \multicolumn{1}{c}{[0-19]} & \multicolumn{1}{c}{[20-39]} & \multicolumn{1}{c}{[40-59]} & \multicolumn{1}{c}{[60-79]} & \multicolumn{1}{c}{[80-100]}\\
-\midrule
-Agreeableness & 6.14 & 5.21 & 5.29 & 5.40 & 5.43\\
-Conscientiousness & 5.50 & 5.31 & 5.60 & 5.77 & 6.00\\
-Emotional stability & 4.29 & 4.67 & 5.09 & 4.85 & 5.62\\
-Extraversion & 2.79 & 3.67 & 3.61 & 3.42 & 3.50\\
-Openness to experiences & 6.43 & 5.44 & 5.12 & 5.05 & 5.21\\
-\bottomrule
-\addlinespace
-\end{tabular}
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Personality trait scores reported on a 1-7 scale.}
-\end{tablenotes}
-\end{threeparttable}
-\end{center}
-\end{table}
+Given that these personality traits have been found to predict a
+multitude of cognitions and behaviors, from well-being to cognitive
+abilities (Barlett \& Anderson, 2012; Curtis, Windsor, \& Soubelet,
+2015; Hayes \& Joseph, 2003), previous studies have looked at whether
+personality can predict political beliefs and affiliation (Hirsh,
+DeYoung, Xu, \& Peterson, 2010; Jost, West, \& Gosling, 2009). The most
+robust findings are that openness to experience is positively correlated
+with liberalness (Carney, Jost, Gosling, \& Potter, 2008; Ekehammar,
+Akrami, Gylje, \& Zakrisson, 2004), while conscientiousness is
+positively correlated with conservativeness (Barbaranelli, Caprara,
+Vecchione, \& Fraley, 2007; Stenner, 2005).
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:linearmodels_conservatism_ocean_tables}Regression Table Predicting Social Conservatism From Big-Five Personality Traits.}
-\begin{tabular}{lllll}
-\toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(125)$} & \multicolumn{1}{c}{$p$}\\
-\midrule
-Intercept & 25.82 & $[0.07$, $51.58]$ & 1.98 & .049\\
-Openness to experiences & -3.73 & $[-7.50$, $0.04]$ & -1.96 & .052\\
-Conscientiousness & 0.07 & $[-3.98$, $4.11]$ & 0.03 & .974\\
-Extraversion & 1.56 & $[-1.42$, $4.55]$ & 1.04 & .302\\
-Agreeableness & 3.93 & $[0.69$, $7.17]$ & 2.40 & .018\\
-Emotional stability & 4.30 & $[0.70$, $7.91]$ & 2.37 & .020\\
-\bottomrule
-\addlinespace
-\end{tabular}
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Residual standard error: 25.13 on 125 degrees of freedom.
-Multiple R-squared: 0.168, Adjusted R-squared: 0.135. F(5, 125): 5.051, p-value: 0.0003.}
-\end{tablenotes}
-\end{threeparttable}
-\end{center}
-\end{table}
+This project uses data from a larger study that measured political
+beliefs and the big five personality traits. Consistent with prior
+research, we hypothesize that we will find a positive relation between
+conscientiousness and conservatism and a negative relation between
+openness to experience and conservatism. We will first make exploratory
+tables and plots that explore the relation between all big five
+personality traits and social and economic conservatism, and then we
+will run two linear models with traits as predictors and types of
+conservatism as outcome variables.
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:linearmodels_conservatism_ocean_tables}Regression Table Predicting Economic Conservatism From Big-Five Personality Traits.}
-\begin{tabular}{lllll}
-\toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(125)$} & \multicolumn{1}{c}{$p$}\\
-\midrule
-Intercept & 56.54 & $[34.71$, $78.37]$ & 5.13 & < .001\\
-Openness to experiences & -3.79 & $[-6.98$, $-0.59]$ & -2.35 & .021\\
-Conscientiousness & 1.78 & $[-1.65$, $5.20]$ & 1.03 & .307\\
-Extraversion & 0.61 & $[-1.92$, $3.14]$ & 0.48 & .632\\
-Agreeableness & -1.13 & $[-3.88$, $1.61]$ & -0.82 & .415\\
-Emotional stability & 2.34 & $[-0.71$, $5.39]$ & 1.52 & .131\\
-\bottomrule
-\addlinespace
-\end{tabular}
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Residual standard error: 21.3 on 125 degrees of freedom. Multiple R-squared: 0.081, Adjusted R-squared: 0.044. F(5, 125): 2.207, p-value: 0.058.}
-\end{tablenotes}
-\end{threeparttable}
-\end{center}
-\end{table}
-
-\section{Methods}\label{methods}
+\section{Method}\label{method}
 
@@
 
+\hypertarget{ref-barbaranelli2007voters}{}
+Barbaranelli, C., Caprara, G. V., Vecchione, M., \& Fraley, C. R.
+(2007). Voters' personality traits in presidential elections.
+\emph{Personality and Individual Differences}, \emph{42}(7), 1199--1208.
+
+\hypertarget{ref-barlett2012direct}{}
+Barlett, C. P., \& Anderson, C. A. (2012). Direct and indirect relations
+between the big 5 personality traits and aggressive and violent
+behavior. \emph{Personality and Individual Differences}, \emph{52}(8),
+870--875.
+
 \hypertarget{ref-cacioppo1984efficient}{}
@@
 
+\hypertarget{ref-carney2008secret}{}
+Carney, D. R., Jost, J. T., Gosling, S. D., \& Potter, J. (2008). The
+secret lives of liberals and conservatives: Personality profiles,
+interaction styles, and the things they leave behind. \emph{Political
+Psychology}, \emph{29}(6), 807--840.
+
 \hypertarget{ref-R-rio}{}
@@
 \emph{Rio: A swiss-army knife for data file i/o}.
+
+\hypertarget{ref-curtis2015relationship}{}
+Curtis, R. G., Windsor, T. D., \& Soubelet, A. (2015). The relationship
+between big-5 personality traits and cognitive ability in older
+adults--a review. \emph{Aging, Neuropsychology, and Cognition},
+\emph{22}(1), 42--71.
+
+\hypertarget{ref-ekehammar2004matters}{}
+Ekehammar, B., Akrami, N., Gylje, M., \& Zakrisson, I. (2004). What
+matters most to prejudice: Big five personality, social dominance
+orientation, or right-wing authoritarianism? \emph{European Journal of
+Personality}, \emph{18}(6), 463--482.
 
@@
 
+\hypertarget{ref-goldberg1992development}{}
+Goldberg, L. R. (1992). The development of markers for the big-five
+factor structure. \emph{Psychological Assessment}, \emph{4}(1), 26.
+
 \hypertarget{ref-gosling2003very}{}
@@
 
+\hypertarget{ref-hayes2003big}{}
+Hayes, N., \& Joseph, S. (2003). Big 5 correlates of three measures of
+subjective well-being. \emph{Personality and Individual Differences},
+\emph{34}(4), 723--727.
+
 \hypertarget{ref-R-purrr}{}
@@
 tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\hypertarget{ref-hirsh2010compassionate}{}
+Hirsh, J. B., DeYoung, C. G., Xu, X., \& Peterson, J. B. (2010).
+Compassionate liberals and polite conservatives: Associations of
+agreeableness with political ideology and moral values.
+\emph{Personality and Social Psychology Bulletin}, \emph{36}(5),
+655--664.
+
+\hypertarget{ref-john1999big}{}
+John, O. P., \& Srivastava, S. (1999). The big five trait taxonomy:
+History, measurement, and theoretical perspectives. \emph{Handbook of
+Personality: Theory and Research}, \emph{2}(1999), 102--138.
+
+\hypertarget{ref-jost2009personality}{}
+Jost, J. T., West, T. V., \& Gosling, S. D. (2009). Personality and
+ideology as determinants of candidate preferences and ``obama
+conversion'' in the 2008 us presidential election. \emph{Du Bois Review:
+Social Science Research on Race}, \emph{6}(1), 103--124.
+
+\hypertarget{ref-mccrae1999age}{}
+McCrae, R. R., Costa, P. T., Lima, M. P. de, Simões, A., Ostendorf, F.,
+Angleitner, A., \ldots{} others. (1999). Age differences in personality
+across the adult life span: Parallels in five cultures.
+\emph{Developmental Psychology}, \emph{35}(2), 466.
 
@@
 \emph{24}(7), 1153--1172.
+
+\hypertarget{ref-stenner2005rights}{}
+Stenner, P. (2005). Rights and emotions, or: The importance of having
+the right emotions. \emph{History \& Philosophy of Psychology},
+\emph{7}(1), 1--11.
 
@@
 \url{https://yihui.name/knitr/}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:table1}Mean Personality Trait Scores by Social Conservatism Score}
+\begin{tabular}{llllll}
+\toprule
+ & \multicolumn{5}{c}{Social Conservatism Score} \\
+\cmidrule(r){2-6}
+personality\_trait & \multicolumn{1}{c}{[0-19]} & \multicolumn{1}{c}{[20-39]} & \multicolumn{1}{c}{[40-59]} & \multicolumn{1}{c}{[60-79]} & \multicolumn{1}{c}{[80-100]}\\
+\midrule
+Agreeableness & 4.67 & 5.20 & 4.88 & 5.76 & 5.90\\
+Conscientiousness & 5.37 & 5.44 & 5.32 & 5.84 & 6.03\\
+Emotional stability & 4.07 & 4.38 & 4.82 & 5.50 & 5.57\\
+Extraversion & 2.73 & 3.16 & 3.57 & 3.90 & 3.72\\
+Openness to experiences & 4.93 & 5.40 & 5.43 & 5.25 & 5.12\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Personality trait scores reported on a 1-7 scale.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:table2}Mean Personality Trait Scores by Economic Conservatism Score}
+\begin{tabular}{llllll}
+\toprule
+ & \multicolumn{5}{c}{Economic Conservatism Score} \\
+\cmidrule(r){2-6}
+personality\_trait & \multicolumn{1}{c}{[0-19]} & \multicolumn{1}{c}{[20-39]} & \multicolumn{1}{c}{[40-59]} & \multicolumn{1}{c}{[60-79]} & \multicolumn{1}{c}{[80-100]}\\
+\midrule
+Agreeableness & 6.14 & 5.21 & 5.29 & 5.40 & 5.43\\
+Conscientiousness & 5.50 & 5.31 & 5.60 & 5.77 & 6.00\\
+Emotional stability & 4.29 & 4.67 & 5.09 & 4.85 & 5.62\\
+Extraversion & 2.79 & 3.67 & 3.61 & 3.42 & 3.50\\
+Openness to experiences & 6.43 & 5.44 & 5.12 & 5.05 & 5.21\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Personality trait scores reported on a 1-7 scale.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:table3}Regression Table Predicting Social Conservatism From Big-Five Personality Traits.}
+\begin{tabular}{lllll}
+\toprule
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(125)$} & \multicolumn{1}{c}{$p$}\\
+\midrule
+Intercept & 25.82 & $[0.07$, $51.58]$ & 1.98 & .049\\
+Openness to experiences & -3.73 & $[-7.50$, $0.04]$ & -1.96 & .052\\
+Conscientiousness & 0.07 & $[-3.98$, $4.11]$ & 0.03 & .974\\
+Extraversion & 1.56 & $[-1.42$, $4.55]$ & 1.04 & .302\\
+Agreeableness & 3.93 & $[0.69$, $7.17]$ & 2.40 & .018\\
+Emotional stability & 4.30 & $[0.70$, $7.91]$ & 2.37 & .020\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Residual standard error: 25.13 on 125 degrees of freedom.
+Multiple R-squared: 0.168, Adjusted R-squared: 0.135. F(5, 125): 5.051, p-value: 0.0003.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:table4}Regression Table Predicting Economic Conservatism From Big-Five Personality Traits.}
+\begin{tabular}{lllll}
+\toprule
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(125)$} & \multicolumn{1}{c}{$p$}\\
+\midrule
+Intercept & 56.54 & $[34.71$, $78.37]$ & 5.13 & < .001\\
+Openness to experiences & -3.79 & $[-6.98$, $-0.59]$ & -2.35 & .021\\
+Conscientiousness & 1.78 & $[-1.65$, $5.20]$ & 1.03 & .307\\
+Extraversion & 0.61 & $[-1.92$, $3.14]$ & 0.48 & .632\\
+Agreeableness & -1.13 & $[-3.88$, $1.61]$ & -0.82 & .415\\
+Emotional stability & 2.34 & $[-0.71$, $5.39]$ & 1.52 & .131\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Residual standard error: 21.3 on 125 degrees of freedom. Multiple R-squared: 0.081, Adjusted R-squared: 0.044. F(5, 125): 2.207, p-value: 0.058.}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
 

### 2019-12-11 scripts/manuscript.Rmd
Merge conflicts

@@
 library(viridis)
+library(GGally)
 
@@
 ```{r figure1, fig.cap="A correlation heatmap demonstrating the correlations between the Big Five personality traits and social and economic conservatism."}
+
 heatmap(cor_conservatism_ocean,

### 2019-12-11 scripts/manuscript.Rmd
added abstract

@@
 abstract: |
-  Here is where we will write our abstract.
+  Since the development of the Five Factor Model as a framework for measuring and classifying personality, psychology research has been interested in using this framework to examine the relationship between personality and cognitions, mindsets, and behaviors.
+Prior research has attempted to predict political beliefs and affiliations from personality traits, finding that the personality trait of openness to experience is positively correlated with liberalness, while the trait of conscientiousness is positively correlated with conservativeness.
+The current study attempts to replicate these findings in a U.S.
+Amazon Mechanical Turk population using the Ten Item Personality Inventory to measure the Big Five personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability) and a 12-item Social and Economic Conservatism Scale to measure the social and economic dimensions of conservatism.
+Consistent with past research, the current study found that openness to experience was a significant negative predictor of both economic and social conservatism.
+Contrary to past findings, however, we found that agreeableness and emotional stability were both significant positive predictors of social conservatism, and conscientiousness was not a significant predictor of either social or economic conservatism.
+Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits, but they were strongly positively correlated with each other.
 
-keywords          : "keywords"
-wordcount         : "X"
+keywords          : "keywords: personality, openness to experiences, conscientiousness, extraversion, agreeableness, emotional stability, conservatism, social conservatism, economic conservatism"
+wordcount         : "208"
 bibliography      : ["r-references.bib"]
@@
 We found that agreeablessness, $\beta$ = 3.93, *t*(125) = 2.40, *p* = .018, and emotional stability, $\beta$ = 4.30, *t*(125) = 2.37, *p* = .020, significantly predict social conservatism, such that, controlling for the other personality traits, those who scored higher on agreeableness and emotional stability measures tended to also score higher on the social conservatism measure.
-Additionally, openness to experiences margionally predicted social conservatism, $\beta$ = -3.73, *t*(125) = -1.96, *p* = .052, such that, controlling for other personality traits, those who scored higher on conservatism tended to score lower on the openness to experience measure.
+Additionally, openness to experiences marginally predicted social conservatism, $\beta$ = -3.73, *t*(125) = -1.96, *p* = .052, such that, controlling for other personality traits, those who scored higher on conservatism tended to score lower on the openness to experience measure.
 

### 2019-12-11 scripts/manuscript.Rmd
Discussion

@@
 
+Consistent with prior research on personality and political beliefs,  participants in this study  that were higher in economic conservatism produced significantly lower scores on openness to experience.
+This relationship has been described in prior research as a result of the ideas and beliefs surrounding economic conservatism, such as rule following, self-regulation, and order, contradicting the ideas and beliefs surrounding openness to experience, such as creativity and diversity of experience [@carney2008secret; @ekehammar2004matters].
+
+However, inconsistent with prior research and our hypotheses, the negative relationship between social conservatism and openness to experience scores, along with the positive relationships between conscientiousness and both social and economic conservatism were not significant.
+With this subject so heavily studied, the lack of significant results indicates that a replication of the study that includes a power analysis and possibly, an increase in sample size may give us a clearer understanding of the strength and significance of these relationships.
+
+Additional exploratory analysis revealed a significant positive relationship between emotional stability and social conservatism, as well as a positive relationship between agreeableness and social conservatism.
+Prior research indicates that emotional stability is not a significant predictor of  conservatism, and agreeableness is usually negatively correlated with conservatism [@sibley2012personality].
+The departure of these results from previous findings may indicate that there is an increase in positive personality traits associated with conservatism, but the controlling, firm, inhibited characteristics heavily associated with conservatism are not compatible with the change in direction between agreeableness and conservatism.
+
+While the results of this study did not support all of our hypotheses on personality traits and conservatism, the limitations of the study surrounding the self-reporting methods along with the potential low power of the study may help explain the departure of our results from previous findings.
+Future research on this subject would be more informed through the use of  experimental methods and observations of participants to determine behavior that reveals personality traits and level of social and economic conservatism.
+Increasing understanding of the relationship between personality traits and left-right differences could help implement actions that would help diffuse the increasing political polarization currently taking place in the United States.
+
 \newpage

### 2019-12-11 scripts/manuscript.tex
Discussion

--- 2019-12-11 scripts/manuscript.tex
@@
             pdfauthor={Sarah Dimakis, Meghan Siritzky, \& Jamie Yellowtail},
-            pdfkeywords={keywords},
+            pdfkeywords={keywords: personality, openness to experiences, conscientiousness, extraversion, agreeableness, emotional stability, conservatism, social conservatism, economic conservatism},
             pdfborder={0 0 0},
@@
 \textsuperscript{1} University of Oregon}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{keywords: personality, openness to experiences, conscientiousness, extraversion, agreeableness, emotional stability, conservatism, social conservatism, economic conservatism\newline\indent Word count: 208}
 \usepackage{csquotes}
@@
 \abstract{
-Here is where we will write our abstract.
+Since the development of the Five Factor Model as a framework for measuring and classifying personality, psychology research has been interested in using this framework to examine the relationship between personality and cognitions, mindsets, and behaviors.
+Prior research has attempted to predict political beliefs and affiliations from personality traits, finding that the personality trait of openness to experience is positively correlated with liberalness, while the trait of conscientiousness is positively correlated with conservativeness.
+The current study attempts to replicate these findings in a U.S.
+Amazon Mechanical Turk population using the Ten Item Personality Inventory to measure the Big Five personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability) and a 12-item Social and Economic Conservatism Scale to measure the social and economic dimensions of conservatism.
+Consistent with past research, the current study found that openness to experience was a significant negative predictor of both economic and social conservatism.
+Contrary to past findings, however, we found that agreeableness and emotional stability were both significant positive predictors of social conservatism, and conscientiousness was not a significant predictor of either social or economic conservatism.
+Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits, but they were strongly positively correlated with each other.
 
@@
 \maketitle
+
+The Five Factor Model is a widely used framework for measuring and classifying personality into five dimensions (Goldberg, 1992; John \& Srivastava, 1999; McCrae et al., 1999).
+Those who score high in \emph{openness to experiences} tend to describe themselves as curious, deep thinkers compared to those who score low in openness to experience, who describe themselves as traditional and conventional.
+Those who score high in \emph{conscientiousness} are generally reliable and hardworking, while those who score low in conscientiousness tend to be disorganized and impulsive.
+Those high in \emph{extraversion} are talkative and energetic, while those high in introversion are reserved and quiet.
+Those who score high in \emph{agreeableness} describe themselves as kind and trusting, while those who score low in agreeableness say they are quarrelsome and critical.
+And lastly, those who are high in \emph{emotional stability} are calm individuals who handle stress well, while those high in neuroticism tend to be anxious individuals who are easily upset.
+
+Given that these personality traits have been found to predict a multitude of cognitions and behaviors, from well-being to cognitive abilities (Barlett \& Anderson, 2012; Curtis, Windsor, \& Soubelet, 2015; Hayes \& Joseph, 2003), previous studies have looked at whether personality can predict political beliefs and affiliation (Hirsh, DeYoung, Xu, \& Peterson, 2010; Jost, West, \& Gosling, 2009).
+The most robust findings are that openness to experience is positively correlated with liberalness (Carney, Jost, Gosling, \& Potter, 2008; Ekehammar, Akrami, Gylje, \& Zakrisson, 2004), while conscientiousness is positively correlated with conservativeness (Barbaranelli, Caprara, Vecchione, \& Fraley, 2007; Stenner, 2005).
+
+This project uses data from a larger study that measured political beliefs and the big five personality traits.
+Consistent with prior research, we hypothesize that we will find a positive relation between conscientiousness and conservatism and a negative relation between openness to experience and conservatism.
+We will first make exploratory tables and plots that explore the relation between all big five personality traits and social and economic conservatism, and then we will run two linear models with traits as predictors and types of conservatism as outcome variables.
+
+\hypertarget{method}{%
+\section{Method}\label{method}}
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Two-hundred U.S.
+adults were recruited via Amazon Mechanical Turk to participate in a study listed as \enquote{Psychology and society survey.} Participants were removed for completing the survey quicker than predetermined time cutoffs or failing to pass attention checks.
+Of the remaining 131 participants, who were 20 to 68 years old (\emph{M} = 40.55, \emph{SD} = 11.98), 54.2\% identified as female and 45.8\% identified as male, while 77.1\% identified as White of Caucasian, 7.6\% as African American or Black, 6.1\% as Hispanic or Latinx, 5.3\% as Asian or Asian American, 0.8\% as Native American, and 9.2\% as \enquote{Other.} The sample leaned liberal, with 45\% affiliated with the Democratic Party, 23.7\% affiliated with the Republican Party, 22.1\% affiliated with no party, and 9.2\% affiliated with the Green Party, Libertarian Party, or another party.
+The participants were compensated \$1.50 for completing the survey, which took on average 10.43 minutes (\emph{SD} = 3.34).
+
+\hypertarget{material}{%
+\subsection{Material}\label{material}}
+
+\textbf{Personality.} To assess personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability), respondents completed the Ten Item Personality Inventory (Gosling, Rentfrow, \& Swann Jr, 2003).
+Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g.
+\enquote{Extraverted, enthusiastic}; \enquote{Critical, quarrelsome}).
+Respondents rated each statement on a 7-point likert scale (1 = Strongly Disagree to 7 = Strongly Agree).
+Responses were coded such that higher values reflected greater identification with the personality trait.
+
+\textbf{Social and Economic Conservatism.} To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale (Everett, 2013).
+Participants were asked to indicate the extent to which they feel positively or negatively about seven social issues and five economic issues (eg.
+Abortion; Fiscal Responsibility).
+Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity).
+Responses were coded such that higher values reflected greater levels of conservatism.
+
+\textbf{Additional Measures.} Incidental affect was induced via video clips (Schaefer, Nils, Sanchez, \& Philippot, 2010).
+Clips from \emph{The Shining} and \emph{The Blair Witch Project} were used to induce fear, clips from \emph{Seven} and \emph{Schindler's List} were used to induce anger, and clips from \emph{Blue} were used to induce no emotion.
+Participants also read a speech on the prevalence of homelessness in the United States and a corresponding policy varying in complexity and affiliation.
+
+Participants completed additional measures, including an adjusted PANAS Affect Scale assessing current emotional state (Watson, Clark, \& Tellegen, 1988), the 18-Point Need for Cognition Scale assessing need for cognition (Cacioppo, Petty, \& Feng Kao, 1984), the 10-Point Emotion Regulation Questionnaire assessing the use of two emotional regulation strategies, cognitive reappraisal and expressive supression (Gross \& John, 2003), and demographic information, including gender, ethnicity, age, and political orientation and affiliation.
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+Participants accessed the survey through the Amazon Mechanical Turk website.
+Once informed consent was confirmed, participants were randomly assigned to watch a video intended to induce primarily fear, anger, or no emotion.
+After watching the video, each participant was presented with information describing the prevalance of homelessness in the United States.
+Participants were then randomly assigned to read a policy statement addressing homelessness that was either simple or complex, and liberal or conservative, and were then asked to answer questions measuring their beliefs about the policy.
+Additional measures followed measuring social and economic conservatism, personality traits, current affective state, neeed for cognition, and emotional regulation.
+Participants concluded the study by providing demographic information.
+
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
+
+We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}forcats} {[}@\}R-forcats{]}, \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{GGally} (Version 1.4.0; Schloerke et al., 2018), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+In order to explore relation between conservatism and personality, we created a table of the Big Five personality trait (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability) scores across different levels of social (see Table 1) and economic (see Table 2) conservatism.
+
+To see whether there were significant relations between social conservatism and the Big Five traits, we then ran a multiple regression predicting social conservatism from the Big Five personality traits.
+We found that together the personality traits explain about 13.5\% of the variance in social conservatism scores, \emph{F}(5, 125) = 5.05, \emph{p} \textless{} .001, with an adjusted \(R^2\) of .14 (see Table 3).
+We found that agreeablessness, \(\beta\) = 3.93, \emph{t}(125) = 2.40, \emph{p} = .018, and emotional stability, \(\beta\) = 4.30, \emph{t}(125) = 2.37, \emph{p} = .020, significantly predict social conservatism, such that, controlling for the other personality traits, those who scored higher on agreeableness and emotional stability measures tended to also score higher on the social conservatism measure.
+Additionally, openness to experiences marginally predicted social conservatism, \(\beta\) = -3.73, \emph{t}(125) = -1.96, \emph{p} = .052, such that, controlling for other personality traits, those who scored higher on conservatism tended to score lower on the openness to experience measure.
+
+To see whether there were significant relations between economic conservatism and the Big Five traits, we then ran a multiple regression predicting economic conservatism from the Big Five personality traits.
+The personality traits taken together did not significantly explain variance in economic conservatism scores, \emph{F}(5, 125) = 2.21, \emph{p} = .058 (see Table 4).
+However, openness to experience was a significant predictor of economic conservatism, \(\beta\) = -3.79, \emph{t}(125) = -2.35, \emph{p} = .021, such that, controlling for other personality traits, those who scored high on economic conservatism subscale tended to score lower on the openness to experiences measure.
+
+To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be \emph{r} = .65.
+Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits (see Figure 1).
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+Consistent with prior research on personality and political beliefs, participants in this study that were higher in economic conservatism produced significantly lower scores on openness to experience.
+This relationship has been described in prior research as a result of the ideas and beliefs surrounding economic conservatism, such as rule following, self-regulation, and order, contradicting the ideas and beliefs surrounding openness to experience, such as creativity and diversity of experience (Carney et al., 2008; Ekehammar et al., 2004).
+
+However, inconsistent with prior research and our hypotheses, the negative relationship between social conservatism and openness to experience scores, along with the positive relationships between conscientiousness and both social and economic conservatism were not significant.
+With this subject so heavily studied, the lack of significant results indicates that a replication of the study that includes a power analysis and possibly, an increase in sample size may give us a clearer understanding of the strength and significance of these relationships.
+
+Additional exploratory analysis revealed a significant positive relationship between emotional stability and social conservatism, as well as a positive relationship between agreeableness and social conservatism.
+Prior research indicates that emotional stability is not a significant predictor of conservatism, and agreeableness is usually negatively correlated with conservatism (Sibley, Osborne, \& Duckitt, 2012).
+The departure of these results from previous findings may indicate that there is an increase in positive personality traits associated with conservatism, but the controlling, firm, inhibited characteristics heavily associated with conservatism are not compatible with the change in direction between agreeableness and conservatism.
+
+While the results of this study did not support all of our hypotheses on personality traits and conservatism, the limitations of the study surrounding the self-reporting methods along with the potential low power of the study may help explain the departure of our results from previous findings.
+Future research on this subject would be more informed through the use of experimental methods and observations of participants to determine behavior that reveals personality traits and level of social and economic conservatism.
+Increasing understanding of the relationship between personality traits and left-right differences could help implement actions that would help diffuse the increasing political polarization currently taking place in the United States.
+
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-barbaranelli2007voters}{}%
+Barbaranelli, C., Caprara, G. V., Vecchione, M., \& Fraley, C. R. (2007). Voters' personality traits in presidential elections. \emph{Personality and Individual Differences}, \emph{42}(7), 1199--1208.
+
+\leavevmode\hypertarget{ref-barlett2012direct}{}%
+Barlett, C.
+P., \& Anderson, C.
+A.
+(2012).
+Direct and indirect relations between the big 5 personality traits and aggressive and violent behavior.
+\emph{Personality and Individual Differences}, \emph{52}(8), 870--875.
+
+\leavevmode\hypertarget{ref-cacioppo1984efficient}{}%
+Cacioppo, J. T., Petty, R. E., \& Feng Kao, C. (1984). The efficient assessment of need for cognition. \emph{Journal of Personality Assessment}, \emph{48}(3), 306--307.
+
+\leavevmode\hypertarget{ref-carney2008secret}{}%
+Carney, D.
+R., Jost, J.
+T., Gosling, S.
+D., \& Potter, J.
+(2008).
+The secret lives of liberals and conservatives: Personality profiles, interaction styles, and the things they leave behind.
+\emph{Political Psychology}, \emph{29}(6), 807--840.
+
+\leavevmode\hypertarget{ref-R-rio}{}%
+Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.
+
+\leavevmode\hypertarget{ref-curtis2015relationship}{}%
+Curtis, R.
+G., Windsor, T.
+D., \& Soubelet, A.
+(2015).
+The relationship between big-5 personality traits and cognitive ability in older adults--a review.
+\emph{Aging, Neuropsychology, and Cognition}, \emph{22}(1), 42--71.
+
+\leavevmode\hypertarget{ref-ekehammar2004matters}{}%
+Ekehammar, B., Akrami, N., Gylje, M., \& Zakrisson, I.
+(2004).
+What matters most to prejudice: Big five personality, social dominance orientation, or right-wing authoritarianism?
+\emph{European Journal of Personality}, \emph{18}(6), 463--482.
+
+\leavevmode\hypertarget{ref-everett201312}{}%
+Everett, J. A. (2013). The 12 item social and economic conservatism scale (secs). \emph{PloS One}, \emph{8}(12), e82131.
+
+\leavevmode\hypertarget{ref-R-janitor}{}%
+Firke, S. (2019). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
+
+\leavevmode\hypertarget{ref-R-viridis}{}%
+Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}
+
+\leavevmode\hypertarget{ref-R-viridisLite}{}%
+Garnier, S. (2018b). \emph{ViridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}
+
+\leavevmode\hypertarget{ref-goldberg1992development}{}%
+Goldberg, L. R. (1992). The development of markers for the big-five factor structure. \emph{Psychological Assessment}, \emph{4}(1), 26.
+
+\leavevmode\hypertarget{ref-gosling2003very}{}%
+Gosling, S. D., Rentfrow, P. J., \& Swann Jr, W. B. (2003). A very brief measure of the big-five personality domains. \emph{Journal of Research in Personality}, \emph{37}(6), 504--528.
+
+\leavevmode\hypertarget{ref-gross2003individual}{}%
+Gross, J.
+J., \& John, O.
+P.
+(2003).
+Individual differences in two emotion regulation processes: Implications for affect, relationships, and well-being.
+\emph{Journal of Personality and Social Psychology}, \emph{85}(2), 348.
+
+\leavevmode\hypertarget{ref-hayes2003big}{}%
+Hayes, N., \& Joseph, S. (2003). Big 5 correlates of three measures of subjective well-being. \emph{Personality and Individual Differences}, \emph{34}(4), 723--727.
+
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\hypertarget{ref-hirsh2010compassionate}{}%
+Hirsh, J.
+B., DeYoung, C.
+G., Xu, X., \& Peterson, J.
+B.
+(2010).
+Compassionate liberals and polite conservatives: Associations of agreeableness with political ideology and moral values.
+\emph{Personality and Social Psychology Bulletin}, \emph{36}(5), 655--664.
+
+\leavevmode\hypertarget{ref-john1999big}{}%
+John, O. P., \& Srivastava, S. (1999). The big five trait taxonomy: History, measurement, and theoretical perspectives. \emph{Handbook of Personality: Theory and Research}, \emph{2}(1999), 102--138.
+
+\leavevmode\hypertarget{ref-jost2009personality}{}%
+Jost, J.
+T., West, T.
+V., \& Gosling, S.
+D.
+(2009).
+Personality and ideology as determinants of candidate preferences and ``obama conversion'' in the 2008 us presidential election.
+\emph{Du Bois Review: Social Science Research on Race}, \emph{6}(1), 103--124.
+
+\leavevmode\hypertarget{ref-mccrae1999age}{}%
+McCrae, R.
+R., Costa, P.
+T., Lima, M.
+P.
+de, Simões, A., Ostendorf, F., Angleitner, A., \ldots{} others.
+(1999).
+Age differences in personality across the adult life span: Parallels in five cultures.
+\emph{Developmental Psychology}, \emph{35}(2), 466.
+
+\leavevmode\hypertarget{ref-R-here}{}%
+Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}
+
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-R-psych}{}%
+Revelle, W.
+(2018).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
+\leavevmode\hypertarget{ref-schaefer2010}{}%
+Schaefer, A., Nils, F., Sanchez, X., \& Philippot, P.
+(2010).
+Assessing the effectiveness of a large database of emotion-eliciting films: A new tool for emotion researchers.
+\emph{Cognition and Emotion}, \emph{24}(7), 1153--1172.
+
+\leavevmode\hypertarget{ref-R-GGally}{}%
+Schloerke, B., Crowley, J., Cook, D., Briatte, F., Marbach, M., Thoen, E., \ldots{} Larmarange, J.
+(2018).
+\emph{GGally: Extension to 'ggplot2'}.
+Retrieved from \url{https://CRAN.R-project.org/package=GGally}
+
+\leavevmode\hypertarget{ref-sibley2012personality}{}%
+Sibley, C.
+G., Osborne, D., \& Duckitt, J.
+(2012).
+Personality and political orientation: Meta-analysis and test of a threat-constraint model.
+\emph{Journal of Research in Personality}, \emph{46}(6), 664--677.
+
+\leavevmode\hypertarget{ref-stenner2005rights}{}%
+Stenner, P. (2005). Rights and emotions, or: The importance of having the right emotions. \emph{History \& Philosophy of Psychology}, \emph{7}(1), 1--11.
+
+\leavevmode\hypertarget{ref-watson1988development}{}%
+Watson, D., Clark, L.
+A., \& Tellegen, A.
+(1988).
+Development and validation of brief measures of positive and negative affect: The panas scales.
+\emph{Journal of Personality and Social Psychology}, \emph{54}(6), 1063.
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
 
@@
 \begin{threeparttable}
-\caption{\label{tab:linearmodels_conservatism_ocean_tables}Regression Table Predicting Social Conservatism From Big-Five Personality Traits.}
+\caption{\label{tab:table3}Regression Table Predicting Social Conservatism From Big-Five Personality Traits.}
 \begin{tabular}{lllll}
@@
 \begin{threeparttable}
-\caption{\label{tab:linearmodels_conservatism_ocean_tables}Regression Table Predicting Economic Conservatism From Big-Five Personality Traits.}
+\caption{\label{tab:table4}Regression Table Predicting Economic Conservatism From Big-Five Personality Traits.}
 \begin{tabular}{lllll}
@@
 \end{table}
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Two-hundred U.S.
-adults were recruited via Amazon Mechanical Turk to participate in a study listed as \enquote{Psychology and society survey.} Participants were removed for completing the survey quicker than predetermined time cutoffs or failing to pass attention checks.
-Of the remaining 131 participants, who were 20 to 68 years old (\emph{M} = 40.55, \emph{SD} = 11.98), 54.2\% identified as female and 45.8\% identified as male, while 77.1\% identified as White of Caucasian, 7.6\% as African American or Black, 6.1\% as Hispanic or Latinx, 5.3\% as Asian or Asian American, 0.8\% as Native American, and 9.2\% as \enquote{Other.} The sample leaned liberal, with 45\% affiliated with the Democratic Party, 23.7\% affiliated with the Republican Party, 22.1\% affiliated with no party, and 9.2\% affiliated with the Green Party, Libertarian Party, or another party.
-The participants were compensated \$1.50 for completing the survey, which took on average 10.43 minutes (\emph{SD} = 3.34).
-
-\hypertarget{material}{%
-\subsection{Material}\label{material}}
-
-\textbf{Personality.} To assess personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability), respondents completed the Ten Item Personality Inventory (Gosling, Rentfrow, \& Swann Jr, 2003).
-Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g.
-\enquote{Extraverted, enthusiastic}; \enquote{Critical, quarrelsome}).
-Respondents rated each statement on a 7-point likert scale (1 = Strongly Disagree to 7 = Strongly Agree).
-Responses were coded such that higher values reflected greater identification with the personality trait.
-
-\textbf{Social and Economic Conservatism.} To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale (Everett, 2013).
-Participants were asked to indicate the extent to which they feel positively or negatively about seven social issues and five economic issues (eg.
-Abortion; Fiscal Responsibility).
-Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity).
-Responses were coded such that higher values reflected greater levels of conservatism.
-
-\textbf{Additional Measures.} Incidental affect was induced via video clips (Schaefer, Nils, Sanchez, \& Philippot, 2010).
-Clips from \emph{The Shining} and \emph{The Blair Witch Project} were used to induce fear, clips from \emph{Seven} and \emph{Schindler's List} were used to induce anger, and clips from \emph{Blue} were used to induce no emotion.
-Participants also read a speech on the prevalence of homelessness in the United States and a corresponding policy varying in complexity and affiliation.
-
-Participants completed additional measures, including an adjusted PANAS Affect Scale assessing current emotional state (Watson, Clark, \& Tellegen, 1988), the 18-Point Need for Cognition Scale assessing need for cognition (Cacioppo, Petty, \& Feng Kao, 1984), the 10-Point Emotion Regulation Questionnaire assessing the use of two emotional regulation strategies, cognitive reappraisal and expressive supression (Gross \& John, 2003), and demographic information, including gender, ethnicity, age, and political orientation and affiliation.
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-Participants accessed the survey through the Amazon Mechanical Turk website.
-Once informed consent was confirmed, participants were randomly assigned to watch a video intended to induce primarily fear, anger, or no emotion.
-After watching the video, each participant was presented with information describing the prevalance of homelessness in the United States.
-Participants were then randomly assigned to read a policy statement addressing homelessness that was either simple or complex, and liberal or conservative, and were then asked to answer questions measuring their beliefs about the policy.
-Additional measures followed measuring social and economic conservatism, personality traits, current affective state, neeed for cognition, and emotional regulation.
-Participants concluded the study by providing demographic information.
-
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
-
-We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-In order to explore relation between conservatism and personality, we created a table of the Big Five personality trait (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability) scores across different levels of social (see Table 1) and economic (see Table 2) conservatism.
-
-To see whether there were significant relations between social conservatism and the Big Five traits, we then ran a multiple regression predicting social conservatism from the Big Five personality traits.
-We found that together the personality traits explain about 13.5\% of the variance in social conservatism scores, \emph{F}(5, 125) = 5.05, \emph{p} \textless{} .001, with an adjusted \(R^2\) of .14 (see Table 3).
-We found that agreeablessness, \(\beta\) = 3.93, \emph{t}(125) = 2.40, \emph{p} = .018, and emotional stability, \(\beta\) = 4.30, \emph{t}(125) = 2.37, \emph{p} = .020, significantly predict social conservatism, such that, controlling for the other personality traits, those who scored higher on agreeableness and emotional stability measures tended to also score higher on the social conservatism measure.
-Additionally, openness to experiences margionally predicted social conservatism, \(\beta\) = -3.73, \emph{t}(125) = -1.96, \emph{p} = .052, such that, controlling for other personality traits, those who scored higher on conservatism tended to score lower on the openness to experience measure.
-
-To see whether there were significant relations between economic conservatism and the Big Five traits, we then ran a multiple regression predicting economic conservatism from the Big Five personality traits.
-The personality traits taken together did not significantly explain variance in economic conservatism scores, \emph{F}(5, 125) = 2.21, \emph{p} = .058 (see Table 4).
-However, openness to experience was a significant predictor of economic conservatism, \(\beta\) = -3.79, \emph{t}(125) = -2.35, \emph{p} = .021, such that, controlling for other personality traits, those who scored high on economic conservatism subscale tended to score lower on the openness to experiences measure.
-
-To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be \emph{r} = .65.
-Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits (see Figure 1).
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begin{verbatim}
-## Warning in readLines(file): incomplete final line found on 'r-
-## references.bib'
-\end{verbatim}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
-
-\leavevmode\hypertarget{ref-cacioppo1984efficient}{}%
-Cacioppo, J. T., Petty, R. E., \& Feng Kao, C. (1984). The efficient assessment of need for cognition. \emph{Journal of Personality Assessment}, \emph{48}(3), 306--307.
-
-\leavevmode\hypertarget{ref-R-rio}{}%
-Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.
-
-\leavevmode\hypertarget{ref-everett201312}{}%
-Everett, J. A. (2013). The 12 item social and economic conservatism scale (secs). \emph{PloS One}, \emph{8}(12), e82131.
-
-\leavevmode\hypertarget{ref-R-janitor}{}%
-Firke, S. (2019). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
-
-\leavevmode\hypertarget{ref-R-viridis}{}%
-Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}
-
-\leavevmode\hypertarget{ref-R-viridisLite}{}%
-Garnier, S. (2018b). \emph{ViridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}
-
-\leavevmode\hypertarget{ref-gosling2003very}{}%
-Gosling, S. D., Rentfrow, P. J., \& Swann Jr, W. B. (2003). A very brief measure of the big-five personality domains. \emph{Journal of Research in Personality}, \emph{37}(6), 504--528.
-
-\leavevmode\hypertarget{ref-gross2003individual}{}%
-Gross, J.
-J., \& John, O.
-P.
-(2003).
-Individual differences in two emotion regulation processes: Implications for affect, relationships, and well-being.
-\emph{Journal of Personality and Social Psychology}, \emph{85}(2), 348.
-
-\leavevmode\hypertarget{ref-R-purrr}{}%
-Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
-
-\leavevmode\hypertarget{ref-R-here}{}%
-Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}
-
-\leavevmode\hypertarget{ref-R-tibble}{}%
-Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
-
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
-\leavevmode\hypertarget{ref-R-psych}{}%
-Revelle, W.
-(2018).
-\emph{Psych: Procedures for psychological, psychometric, and personality research}.
-Evanston, Illinois: Northwestern University.
-Retrieved from \url{https://CRAN.R-project.org/package=psych}
-
-\leavevmode\hypertarget{ref-schaefer2010}{}%
-Schaefer, A., Nils, F., Sanchez, X., \& Philippot, P.
-(2010).
-Assessing the effectiveness of a large database of emotion-eliciting films: A new tool for emotion researchers.
-\emph{Cognition and Emotion}, \emph{24}(7), 1153--1172.
-
-\leavevmode\hypertarget{ref-watson1988development}{}%
-Watson, D., Clark, L.
-A., \& Tellegen, A.
-(1988).
-Development and validation of brief measures of positive and negative affect: The panas scales.
-\emph{Journal of Personality and Social Psychology}, \emph{54}(6), 1063.
-
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
-Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
-
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
-Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}
-
-\leavevmode\hypertarget{ref-R-stringr}{}%
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
-
-\leavevmode\hypertarget{ref-R-dplyr}{}%
-Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
-
-\leavevmode\hypertarget{ref-R-tidyr}{}%
-Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
-
-\leavevmode\hypertarget{ref-R-readr}{}%
-Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
-
-\leavevmode\hypertarget{ref-R-knitr}{}%
-Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
 

### 2019-12-11 scripts/manuscript.Rmd
New Heatmap
located in chunk titled "figure1"

@@
 library(viridis)
-library(GGally)
+library(corrplot)
 
@@
 
-```{r figure1, fig.cap="A correlation heatmap demonstrating the correlations between the Big Five personality traits and social and economic conservatism."}
+```{r figure1, fig.cap="A correlation heatmap demonstrating the correlations between the Big Five personality traits and social and economic conservatism.", fig.height = 10, fig.width = 8}
+
+corrplot(cor_conservatism_ocean, order="AOE", method="square", tl.pos="lt", type="upper",        
+tl.col="black", tl.cex=0.6, tl.srt=45, 
+         addCoef.col="black",
+         p.mat = 1-abs(cor_conservatism_ocean), sig.level=1, insig = "blank") 
+```
+
+```{r fig1, fig.cap="A correlation heatmap demonstrating the correlations between the Big Five personality traits and social and economic conservatism."}
 

### 2019-12-11 scripts/manuscript.tex
New Heatmap
located in chunk titled "figure1"

@@
 
-We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}forcats} {[}@\}R-forcats{]}, \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{GGally} (Version 1.4.0; Schloerke et al., 2018), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
+We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}forcats} {[}@\}R-forcats{]}, \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{corrplot2017} (Wei \& Simko, 2017), \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{GGally} (Version 1.4.0; Schloerke et al., 2018), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
 
@@
 
+\leavevmode\hypertarget{ref-R-corrplot2017}{}%
+Wei, T., \& Simko, V. (2017). \emph{R package "corrplot": Visualization of a correlation matrix}. Retrieved from \url{https://github.com/taiyun/corrplot}
+
 \leavevmode\hypertarget{ref-R-ggplot2}{}%
@@
 \centering
+\includegraphics{manuscript_files/figure-latex/fig1-1.pdf}
+\caption{\label{fig:fig1}A correlation heatmap demonstrating the correlations between the Big Five personality traits and social and economic conservatism.}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{manuscript_files/figure-latex/figure2-1.pdf}

### 2019-12-11 scripts/manuscript.Rmd
cleaning up folders

@@
 Contrary to past findings, however, we found that agreeableness and emotional stability were both significant positive predictors of social conservatism, and conscientiousness was not a significant predictor of either social or economic conservatism.
-Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits, but they were strongly positively correlated with each other.
+Neither social nor economic conservatism were strongly correlated with any of the Big Five personality traits, but they were strongly positively correlated with each other.
 
@@
 ```{r setup, include = FALSE}
+#install.packages(c("corrplot", "MBESS", "psych"))
 library(papaja)
@@
 Consistent with prior research on personality and political beliefs,  participants in this study  that were higher in economic conservatism produced significantly lower scores on openness to experience.
-This relationship has been described in prior research as a result of the ideas and beliefs surrounding economic conservatism, such as rule following, self-regulation, and order, contradicting the ideas and beliefs surrounding openness to experience, such as creativity and diversity of experience [@carney2008secret; @ekehammar2004matters].
+This relation has been described in prior research as a result of the ideas and beliefs surrounding economic conservatism, such as rule following, self-regulation, and order, contradicting the ideas and beliefs surrounding openness to experience, such as creativity and diversity of experience [@carney2008secret; @ekehammar2004matters].
 

### 2019-12-11 scripts/manuscript.tex
cleaning up folders

--- 2019-12-11 scripts/manuscript.tex
@@
             pdfauthor={Sarah Dimakis, Meghan Siritzky, \& Jamie Yellowtail},
-            pdfkeywords={keywords},
+            pdfkeywords={keywords: personality, openness to experiences, conscientiousness,
+extraversion, agreeableness, emotional stability, conservatism, social
+conservatism, economic conservatism},
             pdfborder={0 0 0},
@@
 \abstract{
-Here is where we will write our abstract.
+Since the development of the Five Factor Model as a framework for
+measuring and classifying personality, psychology research has been
+interested in using this framework to examine the relationship between
+personality and cognitions, mindsets, and behaviors. Prior research has
+attempted to predict political beliefs and affiliations from personality
+traits, finding that the personality trait of openness to experience is
+positively correlated with liberalness, while the trait of
+conscientiousness is positively correlated with conservativeness. The
+current study attempts to replicate these findings in a U.S. Amazon
+Mechanical Turk population using the Ten Item Personality Inventory to
+measure the Big Five personality traits (openness to experiences,
+conscientiousness, extraversion, agreeableness, and emotional stability)
+and a 12-item Social and Economic Conservatism Scale to measure the
+social and economic dimensions of conservatism. Consistent with past
+research, the current study found that openness to experience was a
+significant negative predictor of both economic and social conservatism.
+Contrary to past findings, however, we found that agreeableness and
+emotional stability were both significant positive predictors of social
+conservatism, and conscientiousness was not a significant predictor of
+either social or economic conservatism. Neither social nor economic
+conservatism were strongly correlated with any of the Big Five
+personality traits, but they were strongly positively correlated with
+each other.
 
@@
 We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
-\emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham,
-François, Henry, \& Müller, 2019), \emph{forcats} (Version 0.4.0;
-Wickham, 2019a), \emph{ggplot2} (Version 3.2.1; Wickham, 2016),
-\emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0;
-Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja}
-(Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12;
-Revelle, 2018), \emph{purrr} (Version 0.3.3; Henry \& Wickham, 2019),
+\emph{\}forcats} {[}@\}R-forcats{]}, \emph{\}MBESS} {[}@\}R-MBESS{]},
+\emph{corrplot2017} (Wei \& Simko, 2017), \emph{dplyr} (Version 0.8.3;
+Wickham, François, Henry, \& Müller, 2019), \emph{GGally} (Schloerke et
+al., 2018), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here}
+(Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke,
+2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version
+0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle,
+2018), \emph{purrr} (Version 0.3.3; Henry \& Wickham, 2019),
 \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018),
 \emph{rio} (Version 0.5.16; C.-h. Chan, Chan, Leeper, \& Becker, 2018),
-\emph{stringr} (Version 1.4.0; Wickham, 2019b), \emph{tibble} (Version
+\emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version
 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \&
@@
 measures tended to also score higher on the social conservatism measure.
-Additionally, openness to experiences margionally predicted social
+Additionally, openness to experiences marginally predicted social
 conservatism, \(\beta\) = -3.73, \emph{t}(125) = -1.96, \emph{p} = .052,
@@
 
+Consistent with prior research on personality and political beliefs,
+participants in this study that were higher in economic conservatism
+produced significantly lower scores on openness to experience. This
+relation has been described in prior research as a result of the ideas
+and beliefs surrounding economic conservatism, such as rule following,
+self-regulation, and order, contradicting the ideas and beliefs
+surrounding openness to experience, such as creativity and diversity of
+experience (Carney et al., 2008; Ekehammar et al., 2004).
+
+However, inconsistent with prior research and our hypotheses, the
+negative relationship between social conservatism and openness to
+experience scores, along with the positive relationships between
+conscientiousness and both social and economic conservatism were not
+significant. With this subject so heavily studied, the lack of
+significant results indicates that a replication of the study that
+includes a power analysis and possibly, an increase in sample size may
+give us a clearer understanding of the strength and significance of
+these relationships.
+
+Additional exploratory analysis revealed a significant positive
+relationship between emotional stability and social conservatism, as
+well as a positive relationship between agreeableness and social
+conservatism. Prior research indicates that emotional stability is not a
+significant predictor of conservatism, and agreeableness is usually
+negatively correlated with conservatism (Sibley, Osborne, \& Duckitt,
+2012). The departure of these results from previous findings may
+indicate that there is an increase in positive personality traits
+associated with conservatism, but the controlling, firm, inhibited
+characteristics heavily associated with conservatism are not compatible
+with the change in direction between agreeableness and conservatism.
+
+While the results of this study did not support all of our hypotheses on
+personality traits and conservatism, the limitations of the study
+surrounding the self-reporting methods along with the potential low
+power of the study may help explain the departure of our results from
+previous findings. Future research on this subject would be more
+informed through the use of experimental methods and observations of
+participants to determine behavior that reveals personality traits and
+level of social and economic conservatism. Increasing understanding of
+the relationship between personality traits and left-right differences
+could help implement actions that would help diffuse the increasing
+political polarization currently taking place in the United States.
+
 \newpage
@@
 \section{References}\label{references}
-
-\begin{verbatim}
-## Warning in readLines(file): incomplete final line found on 'r-
-## references.bib'
-\end{verbatim}
 
@@
 
+\hypertarget{ref-R-GGally}{}
+Schloerke, B., Crowley, J., Cook, D., Briatte, F., Marbach, M., Thoen,
+E., \ldots{} Larmarange, J. (2018). \emph{GGally: Extension to
+'ggplot2'}. Retrieved from
+\url{https://CRAN.R-project.org/package=GGally}
+
+\hypertarget{ref-sibley2012personality}{}
+Sibley, C. G., Osborne, D., \& Duckitt, J. (2012). Personality and
+political orientation: Meta-analysis and test of a threat-constraint
+model. \emph{Journal of Research in Personality}, \emph{46}(6),
+664--677.
+
 \hypertarget{ref-stenner2005rights}{}
@@
 
+\hypertarget{ref-R-corrplot2017}{}
+Wei, T., \& Simko, V. (2017). \emph{R package ``corrplot'':
+Visualization of a correlation matrix}. Retrieved from
+\url{https://github.com/taiyun/corrplot}
+
 \hypertarget{ref-R-ggplot2}{}
@@
 
-\hypertarget{ref-R-forcats}{}
-Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical
-variables (factors)}. Retrieved from
-\url{https://CRAN.R-project.org/package=forcats}
-
 \hypertarget{ref-R-stringr}{}
-Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for
 common string operations}. Retrieved from
@@
 \centering
+\includegraphics{manuscript_files/figure-latex/fig1-1.pdf}
+\caption{\label{fig:fig1}A correlation heatmap demonstrating the
+correlations between the Big Five personality traits and social and
+economic conservatism.}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{manuscript_files/figure-latex/figure2-1.pdf}

### 2019-12-17 scripts/manuscript.Rmd

@@
 The current study attempts to replicate these findings in a U.S.
-Amazon Mechanical Turk population using the Ten Item Personality Inventory to measure the Big Five personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability) and a 12-item Social and Economic Conservatism Scale to measure the social and economic dimensions of conservatism.
+Amazon Mechanical Turk population using the Ten Item Personality Inventory to measure the Big Five personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability), and a 12-item Social and Economic Conservatism Scale to measure the social and economic dimensions of conservatism.
 Consistent with past research, the current study found that openness to experience was a significant negative predictor of both economic and social conservatism.
@@
 tidy <- data %>% 
-  pivot_longer(cols = c(sec_economic_conservatism, sec_social_conservatism),
+  pivot_longer(cols = c(sec_economic_conservatism, sec_social_conservatism), #Nice pivot!
                names_to = "conservatism_type",
@@
                values_to = "conservatism_score") %>% 
-  mutate(conservatism_type = recode(conservatism_type, `economic_conservatism` = "Economic conservatism",
+  mutate(conservatism_type = recode(conservatism_type, 
+                                    `economic_conservatism` = "Economic conservatism",
                                     `social_conservatism` = "Social conservatism")) %>%
@@
 This project uses data from a larger study that measured political beliefs and the big five personality traits.
-Consistent with prior research, we hypothesize that we will find a positive relation between conscientiousness and conservatism and a negative relation between openness to experience and conservatism.
-We will first make exploratory tables and plots that explore the relation between all big five personality traits and social and economic conservatism, and then we will run two linear models with traits as predictors and types of conservatism as outcome variables.
-
+Consistent with prior research, we hypothesize that we would find a positive relation between conscientiousness and conservatism and a negative relation between openness to experience and conservatism.
+We first make exploratory tables and plots that explore the relation between all big five personality traits and social and economic conservatism, and then we run two linear models with traits as predictors and types of conservatism as outcome variables.
+<!-- Nice intro; concise and informative -->
 # Method
-
+<!-- This chunk is great for your inline code -->
 ```{r, include = FALSE}
@@
 sd_age <- sd(as.numeric(data$age)) %>% round(2)
-r1_age <- range(as.numeric(data$age))[1]
-r2_age <- range(as.numeric(data$age))[2]
+r1_age <- range(as.numeric(data$age))[1] #or min(as.numeric(data$age))
+r2_age <- range(as.numeric(data$age))[2] #or max(as.numeric(data$age))
 
@@
 #I'm creating a function that will spit out the percentage of people with a given ethnicity, including a % sign
+##- Whoa, a function! Awesome!
 percent_ethn <- function(pos){
   paste(((table(data$ethnicity)[[pos]]/n) *100) %>% round(1), "%", sep = "")}
-black <-percent_ethn(1)
+black <- percent_ethn(1)
 asian <- percent_ethn(2)
@@
 male <- percent_gen(2)
+
+# This might work to replace all functions
+# percent_fun <- function(var, pos){
+#   paste(((table(data[var])[[pos]]/n) *100) %>% round(1), "%", sep = "")}
+# e.g.,
+# percent_fun("gender", 1)
+# percent_fun("political_affiliation", 1)
 
@@
 adults were recruited via Amazon Mechanical Turk to participate in a study listed as "Psychology and society survey." Participants were removed for completing the survey quicker than predetermined time cutoffs or failing to pass attention checks.
-Of the remaining `r n` participants, who were `r r1_age` to `r r2_age` years old (*M* = `r mean_age`, *SD* = `r sd_age`), `r female` identified as female and `r male` identified as male, while `r white` identified as White of Caucasian, `r black` as African American or Black, `r hispanic` as Hispanic or Latinx, `r asian` as Asian or Asian American, `r native` as Native American, and `r other` as "Other." The sample leaned liberal, with `r democrat` affiliated with the Democratic Party, `r republican` affiliated with the Republican Party, `r no_party` affiliated with no party, and `r other` affiliated with the Green Party, Libertarian Party, or another party.
+Of the remaining `r n` participants, who were `r r1_age` to `r r2_age` years old (*M* = `r mean_age`, *SD* = `r sd_age`), `r female` identified as female and `r male` identified as male, while `r white` identified as White or Caucasian, `r black` as African American or Black, `r hispanic` as Hispanic or Latinx, `r asian` as Asian or Asian American, `r native` as Native American, and `r other` as "Other." The sample leaned liberal, with `r democrat` affiliated with the Democratic Party, `r republican` affiliated with the Republican Party, `r no_party` affiliated with no party, and `r other` affiliated with the Green Party, Libertarian Party, or another party.
 The participants were compensated $1.50 for completing the survey, which took on average `r duration_m` minutes (*SD* = `r duration_sd`).
@@
 To see whether there were significant relations between social conservatism and the Big Five traits, we then ran a multiple regression predicting social conservatism from the Big Five personality traits.
-We found that together the personality traits explain about 13.5% of the variance in social conservatism scores, *F*(5, 125) = 5.05, *p* < .001, with an adjusted $R^2$ of .14 (see Table 3).
+We found that together the personality traits explain about 13.5% of the variance in social conservatism scores, *F*(5, 125) = 5.05, *p* < .001, with an adjusted $R^2$ of .14 <!-- OR `r round(summary(sc_ocean)$adj.r.squared, 2)` Also, take a look at the broom package for using model results -->(see Table 3).
 We found that agreeablessness, $\beta$ = 3.93, *t*(125) = 2.40, *p* = .018, and emotional stability, $\beta$ = 4.30, *t*(125) = 2.37, *p* = .020, significantly predict social conservatism, such that, controlling for the other personality traits, those who scored higher on agreeableness and emotional stability measures tended to also score higher on the social conservatism measure.
@@
 
-Consistent with prior research on personality and political beliefs,  participants in this study  that were higher in economic conservatism produced significantly lower scores on openness to experience.
+Consistent with prior research on personality and political beliefs,  participants in this studythat were higher in economic conservatism produced significantly lower scores on openness to experience.
 This relation has been described in prior research as a result of the ideas and beliefs surrounding economic conservatism, such as rule following, self-regulation, and order, contradicting the ideas and beliefs surrounding openness to experience, such as creativity and diversity of experience [@carney2008secret; @ekehammar2004matters].
@@
       TRUE ~ "[80-100]"))
+
 tidy_table_sc <- tidy_table_sc %>%
@@
 ```
-
+<!-- Your tables are just great -->
 ```{r table2, echo = FALSE, results = "asis"}
@@
       TRUE ~ "[80-100]"))
+
 tidy_table_ec <- tidy_table_ec %>% 
@@
 ```{r table3, echo = FALSE, results = "asis"}
-apa_sc_ocean <- apa_print(sc_ocean)
+apa_sc_ocean <- apa_print(sc_ocean) #Nice use of apa_print!
 apa_sc_ocean$table %>% 
@@
 cor_conservatism_ocean <- round(cor(untidy_cor),2)
-upper_s<-cor_conservatism_ocean
-upper_s[upper.tri(cor_conservatism_ocean)]<-""
-upper_s<-as.data.frame(upper_s) %>%
+upper_s <- cor_conservatism_ocean
+upper_s[upper.tri(cor_conservatism_ocean)] <- "" #nice job here
+upper_s <- as.data.frame(upper_s) %>%
   apa_table(
@@
 ```{r figure1, fig.cap="A correlation heatmap demonstrating the correlations between the Big Five personality traits and social and economic conservatism.", fig.height = 10, fig.width = 8}
-
+# I like this figure a lot!
 corrplot(cor_conservatism_ocean, order="AOE", method="square", tl.pos="lt", type="upper",        
@@
 ```{r figure2, fig.cap= "We found a significant positive relation between emotional stability and social conservatism, a positive relation between agreeableness and social conservatism, and a negative relation between openness to experiences and economic conservatism.", fig.height = 10, fig.width = 8}
+
 ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = conservatism_type)) +

### 2019-12-17 scripts/manuscript.tex

--- 2019-12-11 scripts/manuscript.tex
@@
-\documentclass[man]{apa6}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  man]{apa6}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
   \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
   pdftitle={Personality and political beliefs across the lifespan},
@@
   pdfkeywords={keywords: personality, openness to experiences, conscientiousness, extraversion, agreeableness, emotional stability, conservatism, social conservatism, economic conservatism},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-  \title{Personality and political beliefs across the lifespan}
-    \author{Sarah Dimakis\textsuperscript{1}, Meghan Siritzky\textsuperscript{1}, \& Jamie Yellowtail\textsuperscript{1}}
-    \date{}
-
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \shorttitle{PERSONALITY AND POLITICAL BELIEFS}
@@
 
+\title{Personality and political beliefs across the lifespan}
+\author{Sarah Dimakis\textsuperscript{1}, Meghan Siritzky\textsuperscript{1}, \& Jamie Yellowtail\textsuperscript{1}}
+\date{}
+
 \authornote{This project was completed as part of the EDLD Introduction to Data Science class at the University of Oregon.
@@
 \textbf{Personality.} To assess personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability), respondents completed the Ten Item Personality Inventory (Gosling, Rentfrow, \& Swann Jr, 2003).
-Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g.
-\enquote{Extraverted, enthusiastic}; \enquote{Critical, quarrelsome}).
+Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g.~\enquote{Extraverted, enthusiastic}; \enquote{Critical, quarrelsome}).
 Respondents rated each statement on a 7-point likert scale (1 = Strongly Disagree to 7 = Strongly Agree).
@@
 
-We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}forcats} {[}@\}R-forcats{]}, \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{corrplot2017} (Wei \& Simko, 2017), \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{GGally} (Version 1.4.0; Schloerke et al., 2018), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
+We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}forcats} {[}@\}R-forcats{]}, \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{corrplot2017} (Wei \& Simko, 2017), \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{GGally} (Schloerke et al., 2018), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.3; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.3.0; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.
 
@@
 Consistent with prior research on personality and political beliefs, participants in this study that were higher in economic conservatism produced significantly lower scores on openness to experience.
-This relationship has been described in prior research as a result of the ideas and beliefs surrounding economic conservatism, such as rule following, self-regulation, and order, contradicting the ideas and beliefs surrounding openness to experience, such as creativity and diversity of experience (Carney et al., 2008; Ekehammar et al., 2004).
+This relation has been described in prior research as a result of the ideas and beliefs surrounding economic conservatism, such as rule following, self-regulation, and order, contradicting the ideas and beliefs surrounding openness to experience, such as creativity and diversity of experience (Carney et al., 2008; Ekehammar et al., 2004).
 
